---
title: "Foreign Vessel Port Analysis for Latam countries"
author: "N. Miller, modified by J Fader"
date: "07/19/2023"
output:
  html_document:
    theme: united
    highlight: tango
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      dev = "png",
                      dpi = 300,
                      cache = TRUE)
```

## load packages

```{r echo = FALSE, message=FALSE, warning=FALSE}

load_or_install_libraries <- function(x){
  for( i in x ){
    #  require returns TRUE invisibly if it was able to load package
    if( ! require( i , character.only = TRUE ) ){
      #  If package was not able to be loaded then re-install
      install.packages( i , dependencies = TRUE )
      #  Load package after installing
      require( i , character.only = TRUE )
    }
  }
}

#  Then try/install packages...
load_or_install_libraries( c("tidyverse" , "bigrquery" ,"devtools", "DBI", "glue", "lubridate", "here", "sf", "extrafont", "patchwork", "terra", "rgeos", "ggspatial", "ggrepel", "tibble", "ggplot2",
                             "purr", "readr", "dplyr", "feather") )

# get fishwatch r independently 
# if (!require("fishwatchr")) {devtools::install_github("GlobalFishingWatch/fishwatchr")}
library(fishwatchr)

con <- DBI::dbConnect(bigrquery::bigquery(),
  project = "world-fishing-827",
  use_legacy_sql = FALSE
)
```

## query/load data

```{r message=FALSE, warning=FALSE, include=TRUE}
# voyages_q <- readr::read_file(here::here("queries", "CHL", "CHL_voyages_query.sql"))
# 
# fishwatchr::gfw_query(query = glue::glue(voyages_q, 
#                                                     start_date = start_date,
#                                                     end_date = end_date,
#                                                     year = year,
#                                                     missing_ssvids = missing_ssvids,
#                                                     temp_table = temp_table_voyages,
#                                                     port_iso = country_iso3,
#                                                     prev_visit_search_date = prev_visit_search_date),
#                                  run_query = TRUE,
#                                  con = con)

# v2 == version with panama canal adjustment
CHL_ports_2025 <- fishwatchr::gfw_query(query = here::here("queries", "CHL", "CHL_voyages_query.sql"), run_query = TRUE, con = con)$data

## filter to keep just reefers and specialized reefers for carriers, according to vessel info table
CHL_ports_2025 <- CHL_ports_2025 %>% 
              filter(vessel_class_best == "fishing" | vessel_class_best == "carrier") %>%
              filter(vessel_flag_best != "UNK")

# write_feather(entry_port_c4_v2, here::here("data", "entry_port_c4_v2.feather"))
# entry_port_c4_v2 <- read_feather(here::here("data", "entry_port_c4_v2.feather"))

# set df to use in figures
visits_df <- CHL_ports %>% filter(year != 2025)

CHL_ports_2025 <- CHL_ports %>% filter(year == 2025)
```

## country lists

```{r}
# country_map <- c(
#   "Peru", "Chile", "Colombia", "Ecuador", "Argentina", "Uruguay", "Panama", "Nicaragua",
#   "Guatamala", "Honduras", "El Salvador", "Brasil", "Costa Rica", "Mexico"
# )

country_map <- c("Chile")
# country_map <- c(
#   "Argentina", "Belize", "Brasil", "Chile", "Colombia", 
#   "Costa Rica", "Ecuador", "El Salvador", "French Guiana", "Guatamala", "Guyana",
#   "Honduras", "Mexico", "Nicaragua", "Panama", "Peru", "Suriname", "Uruguay", "Venezuela"
# )
# names(country_map) <- c("PER", "CHL", "COL", "ECU", "ARG", "URY", "PAN", "NIC", "GTM", "HND", "SLV", "BRA", "CRI", "MEX")
names(country_map) <- c("CHL")

  
```

##Port State Profiles \#####################################################################################

### Visits over Time by Foreign Fishing and Carrier Vessels by Port State

```{r message=FALSE, warning=FALSE, include=TRUE}

iso3s <- c("CHL")
limits <- c(300)

# purrr::map(
purrr::map2(
  .x = iso3s,
  .y = limits,
  .f = visits_by_portstate_line,
  df = visits_df,
  country_map = country_map
)

```

### Visits over Time by Foreign Fishing Vessels by Flag State for each Port State

```{r}
safe_visits_to_portstate_by_flag_bar <- purrr::possibly(
  .f = visits_to_portstate_by_flag_bar,
  otherwise = "Error"
)
limits <- c(400)

purrr::map(
  .x = iso3s,
  # .y = limits,
  .f = safe_visits_to_portstate_by_flag_bar,
  df = visits_df,
  country_map = country_map
)

```

### Visits over Time by Foreign Carrier Vessels by Flag Sate for each Port State

```{r}
purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_flag_bar,
  df = visits_df,
  country_map = country_map,
  vessel_type = "carrier"
)

```

### Visits over Time by Foreign Fishing Vessels by Port for each Port State

```{r}

safe_visits_to_portstate_by_port_bar <- purrr::possibly(
  .f = visits_to_portstate_by_port_bar,
  otherwise = "Error"
)

purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_port_bar,
  df = visits_df,
  country_map = country_map,
  vessel_type = "fishing"
)

```

### Visits over Time by Foreign Carrier Vessels by Port for each Port State

```{r}
purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_port_bar,
  df = visits_df,
  country_map = country_map,
  vessel_type = "carrier"
)

```

### Visits over Time by Foreign Fishing Vessels by Vessel Class for each Port State

```{r}
safe_visits_to_portstate_by_gear_bar <- purrr::possibly(
  .f = visits_to_portstate_by_gear_bar,
  otherwise = "Error"
)

purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_gear_bar,
  df = visits_df,
  country_map = country_map
)

safe_visits_to_portstate_by_gear_donut <- purrr::possibly(
  .f = visits_to_portstate_by_gear_donut,
  otherwise = "Error"
)

purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_gear_donut,
  df = visits_df,
  country_map = country_map
)

```

### Visits over Time by Foreign Fishing Vessels by Flag State by Vessel Class for each Port State

```{r}

# safe_visits_to_portstate_by_gear_flag_bar <- purrr::possibly(
#   .f = visits_to_portstate_by_gear_flag_bar,
#   otherwise = "Error"
# )

purrr::map(
  .x = iso3s,
  .f = visits_to_portstate_by_gear_flag_bar,
  df = visits_df,
  country_map = country_map
)

```

## visits by gear type across all ETP countries (port state aggregated)

```{r}
# gear plot for all gear flags in the region OR port states
visits_by_gear_flag_bar <- function(df, vessel_type = "fishing") {
  # renaming so that facet can display in order and with proper titles, probably cleaner ways to do this...
  df <- df %>% 
            mutate(vessel_label = ifelse(vessel_label == "squid_jigger", "Squid Jiggers",
                              ifelse(vessel_label == "trawlers", "Trawlers",
                              ifelse(vessel_label == "tuna_purse_seines", "Tuna Purse Seines",
                              ifelse(vessel_label == "drifting_longlines", "Drifting Longlines",
                              ifelse(vessel_label == "other_purse_seines", "Other Purse Seines",
                              ifelse(vessel_label == "fishing", "Fishing",
                              ifelse(vessel_label == "set_longlines", "Set Longlines",
                              ifelse(vessel_label == "pole_and_line", "Pole and Line",                            
                              ifelse(vessel_label == "set_gillnets", "Set Gillnets",                            
                              ifelse(vessel_label == "Others", "Others", NA)))))))))))   
  
  top_gear_v <- df %>%
    filter(vessel_class == {{vessel_type}}) %>%
    group_by(vessel_label) %>%
    summarise(grand_total = n(), .groups = "drop") %>%
    # filter(grand_total > 15) %>%
    arrange(desc(grand_total)) %>%
    filter(vessel_label %in% c(
      "Squid Jiggers", "Trawlers", "Tuna Purse Seines", "Drifting Longlines", "Other Purse Seines", 
       "Fishing", "Set Longlines", "Pole and Line", "Set Gillnets"
      # "squid_jigger", "trawlers", "tuna_purse_seines",
      # "drifting_longlines", "other_purse_seines", "fishing",
      # "set_longlines", "pole_and_line", "set_gillnets"
    )) %>%
    pull(vessel_label)
  
    fishing_by_gear_flag_bar <- df %>%
        filter(vessel_class == {{vessel_type}}) %>%
        filter(vessel_label %in% top_gear_v) %>%
        group_by(vessel_flag, vessel_label, year) %>%
        # group_by(vessel_label, year) %>%
        summarize(total = n(), .groups = "drop")
      
    top_flag_state_v <- fishing_by_gear_flag_bar %>%
        group_by(vessel_flag) %>%
        summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
        arrange(desc(grand_total)) %>%
        slice_head(., n = 10) %>%
        distinct(vessel_flag) %>%
        pull(vessel_flag)
      
      others <- fishing_by_gear_flag_bar %>%
        distinct(vessel_flag) %>%
        filter(!vessel_flag %in% top_flag_state_v) %>%
        pull(vessel_flag)
      
      fishing_by_gear_flag_bar <- fishing_by_gear_flag_bar %>%
        mutate(plot_flag = ifelse(vessel_flag %in% top_flag_state_v, vessel_flag, "Others")) %>%
        mutate(plot_flag = factor(plot_flag, levels = c(top_flag_state_v, "Others"))) %>% 
        mutate(vessel_label = factor(vessel_label, levels = c(top_gear_v))) # %>% 
        # mutate(vessel_label = ifelse(vessel_label == "squid_jigger", "Squid Jiggers",
        #                       ifelse(vessel_label == "trawlers", "Trawlers",
        #                       ifelse(vessel_label == "tuna_purse_seines", "Tuna Purse Seines",
        #                       ifelse(vessel_label == "drifting_longlines", "Drifting Longlines",
        #                       ifelse(vessel_label == "other_purse_seines", "Other Purse Seines",
        #                       ifelse(vessel_label == "fishing", "Fishing",
        #                       ifelse(vessel_label == "set_longlines", "Set Longlines",
        #                       ifelse(vessel_label == "pole_and_line", "Pole and Line",                
        #                       ifelse(vessel_label == "set_gillnets", "Set Gillnets",                  
        #                       ifelse(vessel_label == "Others", "Others", NA)))))))))))
        # rank labels by event # so facet orders correctly
      
      p <- ggplot() +
        geom_col(
          data = fishing_by_gear_flag_bar,
          aes(
            x = year,
            y = total,
            fill = plot_flag
          )
        ) +
  scale_x_continuous(limits=c(2012.5,2022.5), breaks = c(2013:2022), expand=c(0,0.2)) +
        scale_fill_manual(
          breaks = c(top_flag_state_v, "Otros"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$chart[5],
            gfw_palettes$secondary[3],
            gfw_palettes$chart[9],
            "gray"
          )
        ) +
        scale_color_manual(
          breaks = c(top_flag_state_v, "Otros"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$chart[5],
            gfw_palettes$secondary[3],
            gfw_palettes$chart[9],
            "gray"
          )
        ) +
        labs(
            title = "Visits by foreign fishing vessel by class and flag across ETP (all port states combined)",
          x = "",
          y = "Number of entry events",
          fill = "",
          caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
        ) +
        theme_gfw() +
        theme(
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          plot.caption = element_text(size = 6, color = "grey45")
        ) +
        facet_wrap(facets = ~vessel_label, scales = "free_y", ncol = 2)
        # facet_wrap(facets = ~reorder(vessel_title, -total), scales = "free_y", ncol = 2)
        p
    }

visits_by_gear_flag_bar(visits_df) 

```

## visits by gear type across all port states

```{r}
# gear plot for all gear flags in the region OR port states
visits_by_gear_port_bar <- function(df, vessel_type = "fishing") {
  # renaming so that facet can display in order and with proper titles, probably cleaner ways to do this...
  df <- df %>% 
            mutate(vessel_label = ifelse(vessel_label == "squid_jigger", "Squid Jiggers",
                              ifelse(vessel_label == "trawlers", "Trawlers",
                              ifelse(vessel_label == "tuna_purse_seines", "Tuna Purse Seines",
                              ifelse(vessel_label == "drifting_longlines", "Drifting Longlines",
                              ifelse(vessel_label == "other_purse_seines", "Other Purse Seines",
                              ifelse(vessel_label == "fishing", "Fishing",
                              ifelse(vessel_label == "set_longlines", "Set Longlines",
                              ifelse(vessel_label == "pole_and_line", "Pole and Line",                            
                              ifelse(vessel_label == "set_gillnets", "Set Gillnets",                            
                              ifelse(vessel_label == "Others", "Others", NA)))))))))))   
  
  top_gear_v <- df %>%
    filter(vessel_class == {{vessel_type}}) %>%
    group_by(vessel_label) %>%
    summarise(grand_total = n(), .groups = "drop") %>%
    # filter(grand_total > 15) %>%
    arrange(desc(grand_total)) %>%
    filter(vessel_label %in% c(
      "Squid Jiggers", "Trawlers", "Tuna Purse Seines", "Drifting Longlines", "Other Purse Seines", 
       "Fishing", "Set Longlines", "Pole and Line", "Set Gillnets"
      # "squid_jigger", "trawlers", "tuna_purse_seines",
      # "drifting_longlines", "other_purse_seines", "fishing",
      # "set_longlines", "pole_and_line", "set_gillnets"
    )) %>%
    pull(vessel_label)
  
    fishing_by_gear_bar <- df %>%
        filter(vessel_class == {{vessel_type}}) %>%
        filter(vessel_label %in% top_gear_v) %>%
        group_by(end_port_iso3, vessel_label, year) %>%
        summarize(total = n(), .groups = "drop")
      
    top_port_state_v <- fishing_by_gear_bar %>%
        group_by(end_port_iso3) %>%
        summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
        arrange(desc(grand_total)) %>%
        slice_head(., n = 10) %>%
        distinct(end_port_iso3) %>%
        pull(end_port_iso3)
      
      others <- fishing_by_gear_bar %>%
        distinct(end_port_iso3) %>%
        filter(!end_port_iso3 %in% top_port_state_v) %>%
        pull(end_port_iso3)
      
      fishing_by_gear_bar <- fishing_by_gear_bar %>%
        mutate(plot_flag = ifelse(end_port_iso3 %in% top_port_state_v, end_port_iso3, "Others")) %>%
        mutate(plot_flag = factor(plot_flag, levels = c(top_port_state_v, "Others"))) %>% 
        mutate(vessel_label = factor(vessel_label, levels = c(top_gear_v))) 
      
      p <- ggplot() +
        geom_col(
          data = fishing_by_gear_bar,
          aes(
            x = year,
            y = total,
            fill = plot_flag
          )
        ) +
  scale_x_continuous(limits=c(2012.5,2022.5), breaks = c(2013:2022), expand=c(0,0.2)) +
        scale_fill_manual(
          breaks = c(top_port_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$chart[5],
            gfw_palettes$secondary[3],
            gfw_palettes$chart[9],
            "gray"
          )
        ) +
        scale_color_manual(
          breaks = c(top_port_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$chart[5],
            gfw_palettes$secondary[3],
            gfw_palettes$chart[9],
            "gray"
          )
        ) +
        labs(
          title = "Visits by foreign fishing vessel by class and port state across ETP",
          x = "",
          y = "Number of entry events",
          fill = "",
          caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
        ) +
        theme_gfw() +
        theme(
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          plot.caption = element_text(size = 6, color = "grey45")
        ) +
        facet_wrap(facets = ~vessel_label, scales = "free_y", ncol = 2)
        # facet_wrap(facets = ~reorder(vessel_title, -total), scales = "free_y", ncol = 2)
        p
    }

visits_by_gear_port_bar(visits_df) 

```

### Visits over Time by Foreign Fishing Vessels by Vessel Class by Port for each Port State

```{r}

safe_visits_to_portstate_by_port_gear_bar <- purrr::possibly(
  .f = visits_to_portstate_by_port_gear_bar,
  otherwise = "Error"
)

purrr::map(
  .x = iso3s,
  .f = safe_visits_to_portstate_by_port_gear_bar,
  df = visits_df,
  country_map = country_map
)

```

### Visits over Time by Foreign Fishing Vessels by Flag State by Port for each Port State

```{r}

safe_visits_to_portstate_by_port_flagstate_bar <- purrr::possibly(
  .f = visits_to_portstate_by_port_flagstate_bar,
  otherwise = "Error"
)

purrr::map(
  .x = iso3s,
  .f = visits_to_portstate_by_port_flagstate_bar,
  df = visits_df,
  country_map = country_map
)

```
