
## load custom functions

```{r}
regional_port_map <- function(df, breaks_c, xlim, ylim, vessel_type = "fishing") {
  visits <- df %>%
    filter(vessel_class_best == {{ vessel_type }}) %>%
    group_by(end_port_label, end_port_iso3) %>%
    summarize(
      lat = mean(start_latitude),
      long = mean(start_longitude),
      total = n()
    )

  bbox <- fishwatchr::transform_box(xlim = xlim,
                                    ylim = ylim,
                                    output_crs = "+proj=eqearth +lon_0=0 +wktext")

  if (vessel_type == "fishing") {
    title_prefix <- "Fishing"
    subtitle_prefix <- "fishing"
  } else {
    title_prefix <- "Carrier"
    subtitle_prefix <- "carrier"
  }

  # cutoffs based on the number of cases
  visits_sf <- visits %>%
    sf::st_as_sf(., coords = c("long", "lat"), crs = 4326) %>%
    fishwatchr::recenter_sf(center = 0)


  gg <-
    ggplot() +
    geom_gfw_land(theme='light') +
    geom_sf(
      data = visits_sf,
      aes(
        size = `total`,
        color = `total`
      ),
      stroke = FALSE,
      alpha = 0.7
    ) +
    scale_size_continuous(
      name = "Port events",
      range = c(1, 8),
      breaks = breaks_c,
      labels = c("1-9", "10-49", "50-99", "100-499", "500+")
      # labels = c("1-4", "5-9", "10-19", "20-49", "50+")
    ) +
    scale_color_viridis_c(
      option = "plasma",
      name = "Port events",
      trans = "log",
      breaks = breaks_c,
      labels = c("1-9", "10-49", "50-99", "100-499", "500+")
      # labels = c("1-4", "5-9", "10-19", "20-49", "50+")
    ) +
    coord_sf(
      xlim = c(
        bbox$box_out[["xmin"]],
        bbox$box_out[["xmax"]]
      ),
      ylim = c(
        bbox$box_out[["ymin"]],
        bbox$box_out[["ymax"]]
      )
    ) +
    theme_gfw_map('light') +
    guides(colour = guide_legend()) +
    labs(
      title = glue::glue("{title_prefix} Port entry events in Q4 2025"),
      subtitle = glue::glue("The bubble colors represent the sum of all port entry events for {subtitle_prefix} vessels")
    ) +
    theme(
      plot.title = element_text(color = "#363C4C", size = 9, face = "bold"),
      plot.subtitle = element_text(color = "#848B9B", size = 6),
      legend.title = element_text(color = "#848B9B")
    ) +
    theme(
      legend.position = c(.13, .4)
    )

  # add_logo(gg,
  #   style = "color",
  #   logo_rel_size = 0.25,
  #   xloc = 0.28,
  #   yloc = 0.2
  # )
}

port_entries_by_port_state_line <- function(df, vessel_type = "fishing") {
  df <- df %>%
    filter(vessel_class_best == {{ vessel_type }}) %>%
    group_by(end_port_iso3, month) %>%
    summarize(Total = n())


  ggplot() +
    geom_line(
      data = df,
      aes(
        x = month,
        y = Total,
        colour = end_port_iso3
      ),
      size = 0.6
    ) +
    scale_color_manual(
      values = c(gfw_palette("tracks"), gfw_palette("secondary")),
      labels = c(
        "BEN" = "Benin",
        "CIV" = "Cote d'Ivoire",
        "GHA" = "Ghana",
        "LBR" = "Liberia",
        "NGA" = "Nigeria",
        "TGO" = "Togo"
        )) +
    labs(
      title = glue::glue("{stringr::str_to_sentence(vessel_type)} Vessels: Number of entry events"),
      x = "",
      y = "Number of entry events",
      colour = "Port State"
    ) +
    scale_x_discrete(limits = c(1:12)) +
    ylim(0, 30)+
    theme_gfw() +
    theme(
      legend.position = "bottom",
      legend.direction = "horizontal"
    )
}

merge_2_plots <- function(plot1, plot2) {
  plot1 +
    plot2 +
    patchwork::plot_layout(
      guides = "collect",
      ncol = 2
    ) &
    theme_gfw() +
      theme(legend.position = "bottom")
}

# function to plot lines

unique_vessel_visits_by_port_state_line <- function(df, vessel_type = "fishing") {
  df <- df %>%
    filter(vessel_class == {{ vessel_type }}) %>%
    group_by(end_port_iso3, year) %>%
    summarize(Total = n_distinct(ssvid))

  ggplot() +
    geom_line(
      data = df,
      aes(
        x = year,
        y = Total,
        colour = end_port_iso3
      ),
      size = 0.6
    ) +
    scale_color_manual(
      values = c(gfw_palette("tracks"), gfw_palette("secondary")),
      labels = c(
        "CHL" = "Chile",
        "COL" = "Colombia",
        "CRI" = "Costa Rica",
        "ECU" = "Ecuador",
        "GTM" = "Guatemala",
        "HND" = "Honduras",
        "MEX" = "Mexico",
        "NIC" = "Nicaragua",
        "PAN" = "Panama",
        "PER" = "Peru",
        "SLV" = "El Salvador" 
        )) +
    labs(
      title = glue::glue("{stringr::str_to_sentence(vessel_type)} Vessels: Number of unique vessels"),
      x = "",
      y = "Number of vessels",
      colour = "Port State"
    ) +
    scale_x_discrete(limits = c(2013:2022)) +
   ylim(0, 500)+
    theme_gfw() +
    theme(
      legend.position = "bottom",
      legend.direction = "horizontal"
    )
}

merge_2_plots <- function(plot1, plot2) {
  plot1 +
    plot2 +
    patchwork::plot_layout(
      guides = "collect",
      ncol = 2
    ) &
    theme_gfw() +
      theme(legend.position = "bottom")
}

# visits_by_portstate_line <- function(df, iso3, country_map) {
visits_by_portstate_line <- function(df, iso3, max_limit, country_map) {
  fishing_vessels_events <-
    df %>%
    filter(end_port_iso3 == {{ iso3 }}) %>%
    group_by(vessel_class, month) %>%
    summarize(Total = n()) %>% 
    tidyr::complete(month=10:12, fill = list(Total = 0))


  p <- ggplot(
    data = fishing_vessels_events,
    aes(x = year, y = Total, colour = vessel_class)
  ) +
    geom_line(size = 0.8) +
    scale_color_manual(values = gfw_palette("primary")) +
    labs(title = country_map[[iso3]],
         x = "",
         y = "Number of entry events",
         colour = "Vessel class") +
    geom_text_repel(aes(label = Total),
      # vjust = -.5, hjust = 0.5,
      point.padding = 5, direction = 'y',
      show.legend = FALSE, size = 3
    ) +
  scale_x_continuous(limits=c(9.5,12.5), breaks = c(10:12), expand=c(0,0.2)) +
    ylim(0, max_limit) +
    theme_gfw() +
    theme(
      legend.position = c(0.85, 1),
      legend.direction = "horizontal",
      panel.grid.minor.y = element_blank(),
      panel.grid.minor.x = element_blank(),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12)
    )
  ggsave(filename = paste(paste("visits_by_portstate_line_", country_map[[iso3]], sep=""), ".png", sep=""), plot = p, path = here("outputs/figures/portstateline"), 
         dpi = 300, width = 8, height = 3.5, units="in")
  p
}







```{r}

visits_by_portstate_line <- function(df, iso3, max_limit, country_map) {
  fishing_vessels_events <-
    df %>%
    filter(end_port_iso3 == {{ iso3 }}) %>%
    group_by(vessel_class_best, year) %>%
    summarize(Total = n()) %>% 
    tidyr::complete(year=2025, fill = list(Total = 0))


  p <- ggplot(
    data = fishing_vessels_events,
    aes(x = year, y = Total, colour = vessel_class_best)
  ) +
    geom_line(size = 0.8) +
    scale_color_manual(values = gfw_palette("primary")) +
    labs(title = country_map[[iso3]],
         x = "",
         y = "Numero de entradas",
         colour = "Vessel class") +
    # geom_text_repel(aes(label = Total),
    #   # vjust = -.5, hjust = 0.5,
    #   point.padding = 5, direction = 'y',
    #   show.legend = FALSE, size = 3
    # ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
    ylim(0, max_limit) +
    theme_gfw() +
    theme(
      legend.position = c(0.85, 1),
      legend.direction = "horizontal",
      panel.grid.minor.y = element_blank(),
      panel.grid.minor.x = element_blank(),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12)
    )
  # ggsave(filename = paste(paste("visits_by_portstate_line_", country_map[[iso3]], sep=""), ".png", sep=""), plot = p, path = here("outputs/PER/figures/portstateline"), 
  #        dpi = 300, width = 8, height = 3.5, units="in")
  p
}

visits_to_portstate_by_flag_bar <- function(df, port_state, country_map,
                                                 vessel_type = "fishing") {
  fishing_by_flag_bar <- df %>%
    filter(vessel_class_best == {{ vessel_type }} & end_port_iso3 == {{ port_state }}) %>%
    group_by(vessel_flag_best, year) %>%
    summarize(total = n(), .groups = "drop")

  top_flag_state_v <- fishing_by_flag_bar %>%
    group_by(vessel_flag_best) %>%
    summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(grand_total)) %>%
    slice_head(., n = 8) %>%
    distinct(vessel_flag_best) %>%
    pull(vessel_flag_best)

  others <- fishing_by_flag_bar %>%
    distinct(vessel_flag_best) %>%
    filter(!vessel_flag_best %in% top_flag_state_v) %>%
    pull(vessel_flag_best)

  fishing_by_flag_bar <- fishing_by_flag_bar %>%
    mutate(plot_flag = ifelse(vessel_flag_best %in% top_flag_state_v, vessel_flag_best, "Otros")) %>%
    mutate(plot_flag = factor(plot_flag, levels = c(top_flag_state_v, "Otros")))

  if (vessel_type == "fishing") {
    title_suffix <- "Visitas por bandera - buques pesqueros extranjeros"
  } else {
    title_suffix <- "Visitas por bandera - buques de transporte extranjeros"
  }

  p <- ggplot() +
    geom_col(
      data = fishing_by_flag_bar,
      aes(
        x = year,
        y = total,
        fill = plot_flag,
        color = plot_flag
      )
    ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
    scale_fill_manual(
      breaks = c(top_flag_state_v, "Otros"),
      values = c(
        gfw_palettes$chart[1],
        gfw_palettes$chart[8],
        gfw_palettes$chart[7],
        gfw_palettes$chart[6],
        gfw_palettes$chart[4],
        gfw_palettes$chart[3],
        gfw_palettes$chart[2],
        gfw_palettes$secondary[3],
        "gray"
      )
    ) +
    scale_color_manual(
      breaks = c(top_flag_state_v, "Otros"),
      values = c(
        gfw_palettes$chart[1],
        gfw_palettes$chart[8],
        gfw_palettes$chart[7],
        gfw_palettes$chart[6],
        gfw_palettes$chart[4],
        gfw_palettes$chart[3],
        gfw_palettes$chart[2],
        gfw_palettes$secondary[3],
        "gray"
      )
    ) +
    # coord_flip() +
    labs(
      title = glue::glue("{country_map[[port_state]]}:  {title_suffix}"),
      x = "",
      y = "Numero de entradas",
      fill = "",
      color = ""
      # caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
    ) +
    theme_gfw() +
    theme(
      legend.position = "bottom",
      # legend.direction="horizontal",
      panel.grid.minor.x = element_blank(),
      plot.caption = element_text(size = 6, color = "grey45"),
      # legend.key.size = unit(0.4, "cm"),
      legend.box.spacing = unit(0, "pt"),
      legend.margin=margin(0,0,0,0),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12)
      # legend.text = element_text(size = 10)
    ) +
    guides(fill = guide_legend(nrow = 2))
    # ggsave(filename = paste("visits_by_flag_bar_", country_map[[port_state]], "_", vessel_type, ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_flag_bar"),
    #        dpi = 300, width = 5.5, height = 4, units="in")
    p
}

visits_to_portstate_by_port_bar <- function(df, port_state, top_n = 5,
                                            country_map, vessel_type) {
  fishing_by_port_bar <- df %>%
    filter(vessel_class_best == {{ vessel_type }} & end_port_iso3 == {{ port_state }}) %>%
    group_by(end_port_label, year) %>%
    summarize(total = n(), .groups = "drop")


  top_port_v <- fishing_by_port_bar %>%
    group_by(end_port_label) %>%
    summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(grand_total)) %>%
    slice_head(., n = top_n) %>%
    distinct(end_port_label) %>%
    pull(end_port_label)

  fishing_by_port_bar <- fishing_by_port_bar %>%
    mutate(plot_port = ifelse(end_port_label %in% top_port_v, end_port_label, "Otros")) %>%
    mutate(plot_port = factor(plot_port, levels = c(top_port_v, "Otros")))

  others <- fishing_by_port_bar %>%
    distinct(end_port_label) %>%
    filter(!end_port_label %in% top_port_v) %>%
    pull(end_port_label)

  if (vessel_type == "fishing") {
    title_suffix <- "Visitas por puerto - Buques pesqueros extranjeros"
  } else {
    title_suffix <- "Visitas por puerto - Buques de transporte extranjeros"
  }

  p <- ggplot() +
    geom_col(
      data = fishing_by_port_bar,
      aes(
        x = year,
        y = total,
        fill = plot_port,
        color = plot_port
      )
    ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
    scale_fill_manual(
      breaks = c(top_port_v, "Otros"),
      values = c(
        gfw_palettes$chart[1],
        gfw_palettes$chart[8],
        gfw_palettes$chart[7],
        gfw_palettes$chart[6],
        gfw_palettes$chart[4],
        gfw_palettes$chart[3],
        gfw_palettes$chart[2],
        gfw_palettes$secondary[3],
        "gray"
      )
    ) +
    scale_color_manual(
      breaks = c(top_port_v, "Otros"),
      values = c(
        gfw_palettes$chart[1],
        gfw_palettes$chart[8],
        gfw_palettes$chart[7],
        gfw_palettes$chart[6],
        gfw_palettes$chart[4],
        gfw_palettes$chart[3],
        gfw_palettes$chart[2],
        gfw_palettes$secondary[3],
        "gray"
      )
    ) +
    # coord_flip() +
    labs(
      title = glue::glue("{country_map[[port_state]]}:  {title_suffix}"),
      x = "",
      y = "Numero de entradas",
      fill = "",
      color = ""
      # caption = glue::glue("Others: {paste0(others, collapse = ', ')}") # turning off 'other' caption as hard to fit all at readable font
    ) +
    theme_gfw() +
    theme(
      legend.position = "bottom",
      legend.direction="horizontal",
      panel.grid.minor.x = element_blank(),
      # plot.caption = element_text(size = 6, color = "grey45"), 
      # legend.key.size = unit(0.4, "cm"),
      legend.box.spacing = unit(0, "pt"),
      legend.margin=margin(0,0,0,0),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12)
      # legend.text = element_text(size = 10)
    ) +
    guides(fill = guide_legend(nrow = 2))
    ggsave(filename = paste("visits_by_port_bar_", country_map[[port_state]], "_", vessel_type, ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_port_bar"),
           dpi = 300, width = 5.5, height = 4, units="in")
    p
}

visits_to_portstate_by_gear_bar <- function(df, port_state, country_map) {
  fishing_by_gear_bar <- df %>%
    filter(vessel_class_best == "fishing" & end_port_iso3 == {{ port_state }}) %>%
    group_by(geartype_best, year) %>%
    summarize(total = n(), .groups = "drop")


  top_gear_v <- fishing_by_gear_bar %>%
    group_by(geartype_best) %>%
    summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(grand_total)) %>%
    slice_head(., n = 9) %>%
    distinct(geartype_best) %>%
    pull(geartype_best)

  others <- fishing_by_gear_bar %>%
    distinct(geartype_best) %>%
    filter(!geartype_best %in% c(
      "squid_jigger", "trawlers", "tuna_purse_seines",
      "drifting_longlines", "other_purse_seines", "fishing",
      "set_longlines", "pole_and_line", "set_gillnets"
    )) %>%
    pull(geartype_best)
    
  fishing_by_gear_bar <- fishing_by_gear_bar %>%
      mutate(plot_gear = ifelse(geartype_best %in% top_gear_v, geartype_best, "Others")) %>%
      mutate(plot_gear = factor(plot_gear, levels = c(top_gear_v, "Others")))

  p <- ggplot() +
    geom_col(
      data = fishing_by_gear_bar,
      aes(
        x = year,
        y = total,
        fill = plot_gear
      )
    ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
    scale_fill_manual(values = c(
      "squid_jigger" = gfw_palettes$chart[5],
      "trawlers" = gfw_palettes$chart[1],
      "tuna_purse_seines" = gfw_palettes$chart[2],
      "drifting_longlines" = gfw_palettes$chart[8],
      "other_purse_seines" = gfw_palettes$chart[7],
      "fishing" = gfw_palettes$chart[6],
      "set_longlines" = gfw_palettes$chart[3],
      "pole_and_line" = gfw_palettes$chart[4],
      "set_gillnets" = gfw_palettes$tracks[2],
      "Others" = "gray"
    ),
    labels=c(
      "squid_jigger" = "Squid Jiggers", 
      "trawlers" = "Trawlers",
      "tuna_purse_seines" = "Tuna Purse Seines",
      "drifting_longlines" = "Drifting Longlines",
      "other_purse_seines" = "Other Purse Seines",
      "fishing" = "Fishing",
      "set_longlines" = "Set Longlines",
      "pole_and_line" = "Pole and Line",
      "set_gillnets" = "Set Gillnets",
      "Others" = "Others")) +
    labs(
      title = glue::glue("{country_map[[port_state]]}: Visits by foreign fishing vessel by class"),
      x = "",
      y = "Numero de entradas",
      fill = "",
      caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
    ) +
    theme_gfw() +
    theme(
      panel.grid.minor.x = element_blank(),
      plot.caption = element_text(size = 8, color = "grey45"),
      axis.text = element_text(size = 10),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 10)
    )
    # ggsave(filename = paste("visits_by_gear_bar_", "_", country_map[[port_state]], ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_gear_bar"),
    #        dpi = 300, width = 8, height = 3.5, units="in")
    p
}

visits_to_portstate_by_gear_flag_bar <- function(df, port_state, country_map, vessel_type = "fishing") {
  # renaming so that facet can display in order and with proper titles, probably cleaner ways to do this...
  df <- df %>% 
            mutate(geartype_best = ifelse(geartype_best == "squid_jigger", "Squid Jiggers",
                              ifelse(geartype_best == "trawlers", "Trawlers",
                              ifelse(geartype_best == "tuna_purse_seines", "Tuna Purse Seines",
                              ifelse(geartype_best == "drifting_longlines", "Drifting Longlines",
                              ifelse(geartype_best == "other_purse_seines", "Other Purse Seines",
                              ifelse(geartype_best == "fishing", "Fishing",
                              ifelse(geartype_best == "set_longlines", "Set Longlines",
                              ifelse(geartype_best == "pole_and_line", "Pole and Line",                            
                              ifelse(geartype_best == "set_gillnets", "Set Gillnets",                            
                              ifelse(geartype_best == "Others", "Others", NA)))))))))))   
  
  top_gear_v <- df %>%
    filter(vessel_class_best == {{vessel_type}} & end_port_iso3 == {{port_state}}) %>%
    group_by(geartype_best) %>%
    summarise(grand_total = n(), .groups = "drop") %>%
    # filter(grand_total > 15) %>%
    arrange(desc(grand_total)) %>% 
    filter(geartype_best %in% c(
      "Squid Jiggers", "Trawlers", "Tuna Purse Seines", "Drifting Longlines", "Other Purse Seines", 
       "Fishing", "Set Longlines", "Pole and Line", "Set Gillnets"
      # "squid_jigger", "trawlers", "tuna_purse_seines",
      # "drifting_longlines", "other_purse_seines", "fishing",
      # "set_longlines", "pole_and_line", "set_gillnets"
    )) %>%
    pull(geartype_best)
  
  
  if (length(top_gear_v) < 1) {
    break } else {
      fishing_by_gear_flag_bar <- df %>%
        filter(vessel_class_best == {{vessel_type}} & end_port_iso3 == {{port_state}}) %>%
        filter(geartype_best %in% top_gear_v) %>%
        group_by(vessel_flag_best, geartype_best, year) %>%
        summarize(total = n(), .groups = "drop")
      
      top_flag_state_v <- fishing_by_gear_flag_bar %>%
        group_by(vessel_flag_best) %>%
        summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
        arrange(desc(grand_total)) %>%
        slice_head(., n = 6) %>%
        distinct(vessel_flag_best) %>%
        pull(vessel_flag_best)
      
      others <- fishing_by_gear_flag_bar %>%
        distinct(vessel_flag_best) %>%
        filter(!vessel_flag_best %in% top_flag_state_v) %>%
        pull(vessel_flag_best)
      
      fishing_by_gear_flag_bar <- fishing_by_gear_flag_bar %>%
        mutate(plot_flag = ifelse(vessel_flag_best %in% top_flag_state_v, vessel_flag_best, "Others")) %>%
        mutate(plot_flag = factor(plot_flag, levels = c(top_flag_state_v, "Others"))) %>% 
        mutate(geartype_best = factor(geartype_best, levels = c(top_gear_v))) # %>% 
        # mutate(vessel_label = ifelse(vessel_label == "squid_jigger", "Squid Jiggers",
        #                       ifelse(vessel_label == "trawlers", "Trawlers",
        #                       ifelse(vessel_label == "tuna_purse_seines", "Tuna Purse Seines",
        #                       ifelse(vessel_label == "drifting_longlines", "Drifting Longlines",
        #                       ifelse(vessel_label == "other_purse_seines", "Other Purse Seines",
        #                       ifelse(vessel_label == "fishing", "Fishing",
        #                       ifelse(vessel_label == "set_longlines", "Set Longlines",
        #                       ifelse(vessel_label == "pole_and_line", "Pole and Line",                
        #                       ifelse(vessel_label == "set_gillnets", "Set Gillnets",                  
        #                       ifelse(vessel_label == "Others", "Others", NA)))))))))))
        # rank labels by event # so facet orders correctly
      
      p <- ggplot() +
        geom_col(
          data = fishing_by_gear_flag_bar,
          aes(
            x = year,
            y = total,
            fill = plot_flag
          )
        ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
        scale_fill_manual(
          breaks = c(top_flag_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$secondary[3],
            "gray"
          )
        ) +
        scale_color_manual(
          breaks = c(top_flag_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$secondary[3],
            "gray"
          )
        ) +
        labs(
          title = glue::glue("{country_map[[port_state]]}: Visitas por arte de pesca y bandera - buques pesqueros extranjeros"),
          x = "",
          y = "Numero de entradas",
          fill = "",
          caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
        ) +
        theme_gfw() +
        theme(
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          plot.caption = element_text(size = 6, color = "grey45")
        ) +
        facet_wrap(facets = ~geartype_best, scales = "free_y", ncol = 2)
        # facet_wrap(facets = ~reorder(vessel_title, -total), scales = "free_y", ncol = 2)
        # ggsave(filename = paste("visits_by_gear_flag_", "_", country_map[[port_state]], ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_gear_flag"),
        #        dpi = 300, width = 8, height = 3.5, units="in")
        p
    }
}



visits_to_portstate_by_port_gear_bar <- function(df, port_state, top_n = 5, country_map, vessel_type = "fishing") {

  top_ports_v <- df %>%
    filter(vessel_class_best == {{ vessel_type }} & end_port_iso3 == {{ port_state }}) %>%
    group_by(end_port_label) %>%
    summarise(grand_total = n(), .groups = "drop") %>%
    arrange(desc(grand_total)) %>% 
    slice_head(., n = top_n) %>%
    distinct(end_port_label) %>%
    pull(end_port_label)

  if (length(top_ports_v) < 1) {
    break
  } else {
    fishing_by_gear_port_bar <- df %>%
      filter(vessel_class_best == {{ vessel_type }} & end_port_iso3 == {{ port_state }}) %>%
      # filter(end_port_label %in% top_ports_v) %>%
      group_by(geartype_best, end_port_label, year) %>%
      summarize(total = n(), .groups = "drop")

    others <- fishing_by_gear_port_bar %>%
      distinct(geartype_best) %>%
      filter(!geartype_best %in% c(
        "squid_jigger", "trawlers", "tuna_purse_seines",
        "drifting_longlines", "other_purse_seines", "fishing",
        "set_longlines", "pole_and_line", "set_gillnets"
      )) %>%
      pull(geartype_best)

    top_gear <- fishing_by_gear_port_bar %>%
      distinct(geartype_best) %>%
      filter(geartype_best %in% c(
        "squid_jigger", "trawlers", "tuna_purse_seines",
        "drifting_longlines", "other_purse_seines", "fishing",
        "set_longlines", "pole_and_line", "set_gillnets"
      )) %>%
      pull(geartype_best)
    
    fishing_by_gear_port_bar <- fishing_by_gear_port_bar %>%
      mutate(plot_gear = ifelse(geartype_best %in% top_gear, geartype_best, "Others")) %>%
      mutate(plot_gear = factor(plot_gear, levels = c(top_gear, "Others"))) %>% 
      mutate(plot_port = ifelse(end_port_label %in% top_ports_v, end_port_label, "Other Ports")) %>% # rank labels by event # so facet orders correctly
      mutate(plot_port = factor(plot_port, levels = c(top_ports_v, "Other Ports")))
    
    p <- ggplot() +
      geom_col(
        data = fishing_by_gear_port_bar,
        aes(
          x = year,
          y = total,
          fill = plot_gear
        )
      ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
      scale_fill_manual(
        values = c(
        "squid_jigger" = gfw_palettes$chart[5],
        "trawlers" = gfw_palettes$chart[1],
        "tuna_purse_seines" = gfw_palettes$chart[2],
        "drifting_longlines" = gfw_palettes$chart[8],
        "other_purse_seines" = gfw_palettes$chart[7],
        "fishing" = gfw_palettes$chart[6],
        "set_longlines" = gfw_palettes$chart[3],
        "pole_and_line" = gfw_palettes$chart[4],
        "set_gillnets" = gfw_palettes$tracks[2],
        "Others" = "gray"
      ),
        labels=c(
        "squid_jigger" = "Squid Jiggers",
        "trawlers" = "Trawlers",
        "tuna_purse_seines" = "Tuna Purse Seines",
        "drifting_longlines" = "Drifting Longlines",
        "other_purse_seines" = "Other Purse Seines",
        "fishing" = "Fishing",
        "set_longlines" = "Set Longlines",
        "pole_and_line" = "Pole and Line",
        "set_gillnets" = "Set Gillnets",
        "Others" = "Other Gear")) +
      
      labs(
        title = glue::glue("{country_map[[port_state]]}: Visitas por clase - buques pesqueros extranjeros"),
        x = "",
        y = "Numero de entradas",
        fill = "",
        caption = glue::glue("Other Gear: {paste0(others, collapse = ', ')}")
      ) +
      theme_gfw() +
      theme(
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.caption = element_text(size = 6, color = "grey45")
      ) +
      facet_wrap(~plot_port, scales = "free_y", ncol = 2)
      # ggsave(filename = paste("visits_by_port_gear_", "_", country_map[[port_state]], ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_port_gear"),
      # dpi = 300, width = 8, height = 3.5, units="in")
      p
  }
}

visits_to_portstate_by_port_flagstate_bar <- function(df, port_state, top_n = 5, country_map, vessel_type = "fishing") {

  top_ports_v <- df %>%
    filter(vessel_class_best == {{ vessel_type }} & end_port_iso3 == {{ port_state }}) %>%
    group_by(end_port_label) %>%
    summarise(grand_total = n(), .groups = "drop") %>%
    arrange(desc(grand_total)) %>% 
    slice_head(., n = top_n) %>%
    distinct(end_port_label) %>%
    pull(end_port_label)

  if (length(top_ports_v) < 1) {
    break } else {
      fishing_by_flag_port_bar <- df %>%
        filter(vessel_class_best == {{vessel_type}} & end_port_iso3 == {{port_state}}) %>%
        # filter(end_port_label %in% top_ports_v) %>%
        group_by(vessel_flag_best, end_port_label, year) %>%
        summarize(total = n(), .groups = "drop")

      top_flag_state_v <- fishing_by_flag_port_bar %>%
        group_by(vessel_flag_best) %>%
        summarize(grand_total = sum(total, na.rm = TRUE), .groups = "drop") %>%
        arrange(desc(grand_total)) %>%
        slice_head(., n = 8) %>%
        distinct(vessel_flag_best) %>%
        pull(vessel_flag_best)

      others <- fishing_by_flag_port_bar %>%
        distinct(vessel_flag_best) %>%
        filter(!vessel_flag_best %in% top_flag_state_v) %>%
        pull(vessel_flag_best)

      fishing_by_flag_port_bar <- fishing_by_flag_port_bar %>%
        mutate(plot_flag = ifelse(vessel_flag_best %in% top_flag_state_v, vessel_flag_best, "Others")) %>%
        mutate(plot_flag = factor(plot_flag, levels = c(top_flag_state_v, "Others"))) %>% 
        mutate(plot_port = ifelse(end_port_label %in% top_ports_v, end_port_label, "Other Ports")) %>% # rank labels by event # so facet orders correctly
        mutate(plot_port = factor(plot_port, levels = c(top_ports_v, "Other Ports")))

      p <- ggplot() +
        geom_col(
          data = fishing_by_flag_port_bar,
          aes(
            x = year,
            y = total,
            fill = plot_flag
          )
        ) +
  scale_x_continuous(limits=c(2015.5,2025.5), breaks = c(2016:2025), expand=c(0,0.2)) +
        scale_fill_manual(
          breaks = c(top_flag_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$secondary[3],
            "gray"
          )
        ) +
        scale_color_manual(
          breaks = c(top_flag_state_v, "Others"),
          values = c(
            gfw_palettes$chart[1],
            gfw_palettes$chart[8],
            gfw_palettes$chart[7],
            gfw_palettes$chart[6],
            gfw_palettes$chart[4],
            gfw_palettes$chart[3],
            gfw_palettes$chart[2],
            gfw_palettes$secondary[3],
            "gray"
          )
        ) +
        labs(
          title = glue::glue("{country_map[[port_state]]}: Visitas por bandera - buques pesqueros extranjeros"),
          x = "",
          y = "Numero de entradas",
          fill = "",
          caption = glue::glue("Others: {paste0(others, collapse = ', ')}")
        ) +
        theme_gfw() +
        theme(
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          plot.caption = element_text(size = 6, color = "grey45")
          # legend.position = c(1,1)
        ) +
        facet_wrap(~plot_port, scales = "free_y", ncol = 2)
        # ggsave(filename = paste("visits_by_port_flag_", "_", country_map[[port_state]], ".png", sep=""), plot=p, path = here("outputs/PER/figures/visits_by_port_flag"),
        # dpi = 300, width = 8, height = 3.5, units="in")
        p
  }
}

visits_to_portstate_by_gear_donut <- function(df, port_state, country_map) {

  fishing_by_gear_donut <- df %>%
    filter(vessel_class == "fishing" & end_port_iso3 == {{ port_state }}) %>%
    group_by(vessel_label) %>%
    summarize(vessels = n(), .groups = "drop")

  if (nrow(fishing_by_gear_donut) < 1) {
    break
  }

  plot_donut_chart(fishing_by_gear_donut,
    group_var = vessel_label,
    value_var = vessels,
    donut_title = glue::glue("{country_map[[port_state]]}:  Fishing vessels \nby vessel class"),
    add_labels = T,
    show_legend = F,
    label_frac = 0.05,
    show_caption = T
  ) +
    scale_fill_manual(values = c(
      "squid_jigger" = gfw_palettes$chart[5],
      "trawlers" = gfw_palettes$chart[1],
      "tuna_purse_seines" = gfw_palettes$chart[2],
      "drifting_longlines" = gfw_palettes$chart[8],
      "other_purse_seines" = gfw_palettes$chart[7],
      "fishing" = gfw_palettes$chart[6],
      "set_longlines" = gfw_palettes$chart[3],
      "pole_and_line" = gfw_palettes$chart[4],
      "set_gillnets" = gfw_palettes$tracks[2],
      "Others" = "gray"
    ))
}



```
