---
title: "Port Fish Carriers"
author: "Max Schofield"
date: "2024-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=F, warning=F, include=FALSE}
load_or_install_libraries <- function(x){
  for( i in x ){
    #  require returns TRUE invisibly if it was able to load package
    if( ! require( i , character.only = TRUE ) ){
      #  If package was not able to be loaded then re-install
      install.packages( i , dependencies = TRUE )
      #  Load package after installing
      require( i , character.only = TRUE )
    }
  }
}

#  Then try/install packages...
load_or_install_libraries( c("tidyverse" , "bigrquery" ,"devtools", "DBI","glue", "lubridate", "here", "sf", "extrafont", "patchwork", "terra", "rgeos", "ggspatial", "gridExtra", "grid") )

# get fishwatch r independently 
if (!require("fishwatchr")) {devtools::install_github("GlobalFishingWatch/fishwatchr")}
library(fishwatchr)

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
```

```{r connection to BQ, echo=F, warning=F, include=FALSE}
con <- DBI::dbConnect(drv = bigrquery::bigquery(), 
                      project = "world-fishing-827", 
                      use_legacy_sql = FALSE)
```

```{r sav fao major shape as sf object}
fao_major <- sf::read_sf(here::here('data','geodata','FAO_AREAS_NOCOASTLINE','FAO_AREAS_NOCOASTLINE.shp')) %>%
  filter(F_LEVEL == 'MAJOR')
```

# Port Fish Carriers 

This notebook is designed to create images illustrating the activities of fish carrier vessels that visit the focal port of the port profile. 

The following images are planned
1. Map/s showing the carrier vessels pattern of life e.g. port-to-port in the region, Europe-Africa, at-sea transhipment. 
i) this requires classifications of the operating model of reefers - this is something TMT can lead. 
2. Map showing the distribution of carrier vessel encounters 
3. Map showing the distribution of carrier vessel loittering

## Pattern of life 

```{r pattern of life track data, echo=F, warning=F}
q_voi_ais <- readr::read_file(file = here::here("queries", "carriers", "carrier_pol_ais.sql"))

voi_ais <- fishwatchr::gfw_query(query = glue::glue(q_voi_ais,
                  start_date = "'2023-01-01'",
                  end_date = "'2024-01-01'"),
                                 run_query = TRUE,
                                 con = con)$data
```


```{r pattern of life plotting params, echo=F, warning=F}
# set plot center
new_center <- -20

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=-20 +wktext"

bbox <- transform_box(
  xlim = c(-60, 15),
  ylim = c(-20, 30),
  # output_crs = fishwatchr::gfw_projections("Equal Earth")$proj_string
  output_crs = best_proj
)

```

```{r pattern of life track map, echo=F, warning=F}
voi_ais_line <- voi_ais %>%
  dplyr::select(ssvid, timestamp, lat, lon) %>%
  sf::st_as_sf(.,
               coords = c("lon", "lat"),
               crs = 4326) %>%
  group_by(ssvid) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)


carrier_map <-
  ggplot() +
  geom_sf(data = voi_ais_line, colour='green') +
    geom_sf(data = fao_major, size = 0.2, alpha = 1, fill = NA, color = 'yellow2') +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  # scale_colour_manual(values=gfw_palettes$tracks) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bbox$box_out[['xmin']], bbox$box_out[['xmax']]),
           ylim = c(bbox$box_out[['ymin']], bbox$box_out[['ymax']]),
           crs = bbox$out_crs)


fishwatchr::add_little_globe(carrier_map,
                             main_box = bbox,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')


ggsave(here::here("outputs", "figures", "carriers", paste("carrier_pol_v",Sys.Date(),".png", sep='')), width = 8, height = 10)

```

## Encnounters

We could consider looking only at at-sea transhipment carriers for the loitering and encounters carrier maps 

```{r download encounters data, echo=F, warning=F}
encounters <- fishwatchr::gfw_query(query = c(
  "SELECT 
    * 
  FROM `world-fishing-827.scratch_hannah.tmt_voyage_enc_sen`
  WHERE 
    main_flag != 'SEN'
    AND other_flag != 'SEN'
        AND (main_class = 'carrier' OR other_vessel_class IN ('carrier'))"),
                                 run_query = TRUE,
                                 con = con)$data
```

```{r encounters point map, echo=F, warning=F}
bbox <- transform_box(
  xlim = c(-60, 15),
  ylim = c(-20, 30),
  output_crs = fishwatchr::gfw_projections("Equal Earth")$proj_string
)

(dakar_carrier_encounters <- encounters %>%
  sf::st_as_sf(., coords = c('mean_lon','mean_lat'), crs = 4326) %>%
  fishwatchr::recenter_sf(.) %>%
ggplot() +
  geom_sf(alpha = 1,
          size = 1.5,
          shape = 21,
          fill = NA,
          color = fishwatchr::gfw_palettes$tracks[9]) +
  geom_sf(data = fao_major,
        size = 0.2,
        alpha = 1,
       fill = NA,
       color = 'yellow2') +
    geom_gfw_land() +
    geom_gfw_eez(size = 0.2,
                 alpha = 1,
                 color = '#ffffff') +
    theme_gfw_map() +
    coord_sf(xlim = c(bbox$box_out[['xmin']], bbox$box_out[['xmax']]),
             ylim = c(bbox$box_out[['ymin']], bbox$box_out[['ymax']]),
             crs = bbox$out_crs) +
    labs(title = glue::glue("Encounters before entering Dakar, Senegal"))
)

ggsave(dakar_carrier_encounters,
       filename = here::here('outputs','figures','carriers',paste('dakar_encounter_map_v',Sys.Date(),'.png', sep='')),
       device = 'png',
       width = 150,
       height = 250,
       units = 'mm',
       dpi = 600)
```

## Loitering 

We need to exclude loitering events that correspond to encounters. 

```{r download loitering data, echo=F, warning=F}
loitering <- fishwatchr::gfw_query(query = c(
  "WITH enc AS (
  SELECT 
    * 
  FROM `world-fishing-827.scratch_hannah.tmt_voyage_enc_sen`
  WHERE 
    main_flag != 'SEN'
    AND other_flag != 'SEN'
        AND (main_class = 'carrier' OR other_vessel_class IN ('carrier'))
), 

loit AS (SELECT 
    * 
  FROM `world-fishing-827.scratch_hannah.tmt_voyage_loit_sen`
  WHERE 
    main_flag != 'SEN'
    AND main_class = 'carrier' 
),

 ----------------------------------------------------------
  -- Identify loitering events that overlap with encounters
  ----------------------------------------------------------
  loitering_with_encounters AS (
    SELECT a.event_id
    FROM (
      SELECT *
      FROM loit
    ) AS a
    JOIN (
      SELECT *
      FROM enc
    ) AS b
    ON (
      (a.vessel_id = b.vessel_id 
      AND b.event_start < a.loitering_end_timestamp
      AND b.event_end >= a.loitering_start_timestamp) OR 
      (a.vessel_id = b.neighbor_vessel_id 
      AND b.event_start < a.loitering_end_timestamp
      AND b.event_end >= a.loitering_start_timestamp)
    )
  ),

  ----------------------------------------------------------
  -- Use this to select for loitering events that don't
  -- overlap
  ----------------------------------------------------------
  loitering_without_encounters AS (
    SELECT *
    FROM loit
    WHERE event_id NOT IN (SELECT event_id FROM loitering_with_encounters)
  )
----------------------------------------------------------
-- Return loitering_carriers
--------------------------------------------------------
SELECT *
FROM loitering_without_encounters
ORDER BY
    ssvid,
    loitering_start_timestamp"),
                                 run_query = TRUE,
                                 con = con)$data
```

```{r loitering point map, echo=F, warning=F}
bbox <- transform_box(
  xlim = c(-60, 15),
  ylim = c(-20, 30),
  output_crs = fishwatchr::gfw_projections("Equal Earth")$proj_string
)

(dakar_carrier_loitering <- loitering %>%
  sf::st_as_sf(., coords = c('start_lon','start_lat'), crs = 4326) %>%
  fishwatchr::recenter_sf(.) %>%
ggplot() +
  geom_sf(alpha = 1,
          size = 1.5,
          shape = 21,
          fill = NA,
          color = fishwatchr::gfw_palettes$tracks[9]) +
  geom_sf(data = fao_major,
        size = 0.2,
        alpha = 1,
       fill = NA,
       color = 'yellow2') +
    geom_gfw_land() +
    geom_gfw_eez(size = 0.2,
                 alpha = 1,
                 color = '#ffffff') +
    theme_gfw_map() +
    coord_sf(xlim = c(bbox$box_out[['xmin']], bbox$box_out[['xmax']]),
             ylim = c(bbox$box_out[['ymin']], bbox$box_out[['ymax']]),
             crs = bbox$out_crs) +
    labs(title = glue::glue("Loitering before entering Dakar, Senegal"))
)

ggsave(dakar_carrier_loitering,
       filename = here::here('outputs','figures','carriers',paste('dakar_loitering_map_v',Sys.Date(),'.png', sep='')),
       device = 'png',
       width = 150,
       height = 250,
       units = 'mm',
       dpi = 600)
```
