---
title: "Port_Program_Quarterly_Q3_2025"
author: "Max Schofield"
date: "2025-10-13"
output: html_document
---

```{=html}
<style>
body {
text-align: left}
</style>
```

# Setup 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=F, warning=F, include=FALSE}
load_or_install_libraries <- function(x){
  for( i in x ){
    #  require returns TRUE invisibly if it was able to load package
    if( ! require( i , character.only = TRUE ) ){
      #  If package was not able to be loaded then re-install
      install.packages( i , dependencies = TRUE )
      #  Load package after installing
      require( i , character.only = TRUE )
    }
  }
}

#  Then try/install packages...
load_or_install_libraries( c("tidyverse" , "bigrquery" ,"devtools", "DBI","glue", "lubridate", "here", "sf", "extrafont", "patchwork", "terra", "rgeos", "ggspatial", "ggrepel", "tibble", "purrr", "stringr") )

# get fishwatch r independently 
if (!require("fishwatchr")) {devtools::install_github("GlobalFishingWatch/fishwatchr")}
library(fishwatchr)
```

```{r connection to BQ, echo=F, warning=F, include=FALSE}
con <- DBI::dbConnect(drv = bigrquery::bigquery(), 
                      project = "world-fishing-827", 
                      use_legacy_sql = FALSE)
```

# Cote Divore  

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}
start_date <- "'2025-07-01 00:00:00 UTC'" 
end_date <- "'2025-09-30 23:59:59 UTC'"
year <- 2025

country_iso3 <- "'CIV'"
# port_name <- "'ABIDJAN'"

prev_visit_search_date <- "'2024-07-01 00:00:00 UTC'" 

# file names
month <- 'Q3'
country <- 'CIV'

# # when to look for previous visits
# prev_visit_search_date <- "'2020-01-01 00:00:00 UTC'" 

# potential MMSIs to force in 
missing_ssvids <- '""'

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.civ_q3_25_all_voyages_temp`'
```


## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_v4.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    year = year,
                                                    missing_ssvids = missing_ssvids,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3,
                                                    prev_visit_search_date = prev_visit_search_date),
                      
                                                    # start_date = start_date,
                                                    # end_date = end_date,
                                                    # year = year,
                                                    # missing_ssvids = missing_ssvids,
                                                    # temp_table = temp_table_voyages,
                                                    # start_year = start_year,
                                                    # end_year = end_year,
                                                    # port_iso = country_iso
                                 run_query = TRUE,
                                 con = con)

```
## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```


## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}
# import QA vessel list from TMT for identity corrections 
civ_ves <- read.csv(here::here("data","TMT_qa_vessel_list", "Master_list_v3_Q3_2025.csv"), header=T) 

# reset ssvid to character
civ_ves$ssvid <- as.character(civ_ves$ssvid)

# Join update data to main data
merged_df <- left_join(voyages_with_coverage, civ_ves, by = "ssvid", suffix = c("", "_tmt"))

#filter(merged_df, ssvid=='412209123')

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}

# filter out the values from the master spreadsheet we shouldn't include
merged_df_inc <- filter(merged_df, Include == 'Yes' | is.na(Include))

# how many rows drop out
nrow(merged_df) - nrow(merged_df_inc)
```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df_inc, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df_inc$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df_inc$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df_inc$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

# write.csv(voyages_url, here::here("data","proactive", paste('GHA_Q2_test','-', Sys.Date(),".csv", sep='')), row.names=F)

```

## add port info
```{r add in port information for CIV using anchorage stops}
anchorages <- fishwatchr::gfw_query(query = c("SELECT s2id, lat, lon, label, sublabel FROM `world-fishing-827.anchorages.named_anchorages_v20240117` WHERE iso3 = 'CIV'"),
                       run_query = TRUE,
                       con = con)$data

# write.csv(anchorages, here::here("data","proactive","2025_q1", paste('Abidjan_anchorages','_', Sys.Date(),".csv", sep='')), row.names=F)

table(anchorages$sublabel)

# s2ids for port features of interest 
vridi <- filter(anchorages, sublabel == 'ABIDJAN VRIDI')$s2id
lagoon <- filter(anchorages, sublabel == 'ABIDJAN LAGOON')$s2id
cargo <- filter(anchorages, sublabel == 'ABIDJAN TREICHVILLE CARGO')$s2id
fish <- filter(anchorages, sublabel == 'ABIDJAN TREICHVILLE FISHING')$s2id
offshore <- filter(anchorages, sublabel %in% c('ABIDJAN OFFSHORE', 'PORT BOUET', 'ABIDJAN PORT BOUET OFFSHORE'))$s2id

# getting bugs so changing order
port_stops <- voyages_url %>%
  rowwise() %>%
  mutate(abj_fishing = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% fish),
         abj_lagoon = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% lagoon),
         abj_vridi = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% vridi),
         abj_cargo = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% cargo),
         abj_offshore = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% offshore))

# table test of outputs 
table(port_stops$abj_fishing)
table(port_stops$abj_vridi)
table(port_stops$abj_offshore)
table(port_stops$abj_cargo)
table(port_stops$abj_lagoon)
```

## formatting
```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(port_stops, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, at_dock=dock, abj_lagoon, abj_vridi, abj_cargo, abj_fishing, abj_offshore, fishing=fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter= encounter, num_encounters=num_encounters, loitering=loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url)
   #gaps=1, num_gaps, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- voyages_reformat$fishing_hs >0

# write out data for initial TMT QA 
write.csv(voyages_reformat, here::here("data", "proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)

```

```{r make adjustments from TMT feedback, echo=F, warning=F, include=FALSE}

write.csv(voyages_filtered, here::here("data", "proactive", "q2_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

## pull fishing data
```{r CIV pull in the fishing data, echo=F, warning=F, include=FALSE}

q_fishing_events <- readr::read_file(here::here("queries","proactive", "proactive_fishing_locations.sql"))

fishing <- fishwatchr::gfw_query(query = glue::glue(q_fishing_events,
                                               voyages_table = "`world-fishing-827.scratch_max.civ_q2_25_all_voyages_temp`" 
                                               ),
                                 run_query = TRUE,
                                 con = con)$data

# sense check the data 
fishing %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

# add gear from TMT review 
gear <- distinct(dplyr::select(voyages_filtered, MMSI, Flag, vessel_type)) %>% 
  mutate(ssvid=as.character(MMSI))

fishing_data <- left_join(fishing, gear, by = join_by(ssvid))

table(fishing_data$vessel_type)

```

```{r CIV voyage activity longline maps, echo=F, warning=F, include=FALSE}
# bin the data
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.5)*0.5
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.5)*0.5


# count positions in each lat lon bin
ps_raster <- 
  # filter out low speeds while vessel in port 
  #filter(fishing_data, vessel_type %in% c('purse_seine_support','tuna_purse_seines')) %>%
  filter(fishing_data, vessel_type %in% c('tuna_purse_seines')) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# look at data distribution
quantile(ps_raster$fishing_hours)

# set upper limit
up_lim <- 200 
#set plot center 
new_center <- 40

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-25, 5),
                          ylim = c(10, -8),
                          output_crs = best_proj)

# map for atlantic longline 
atl_full <- ps_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(atl_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q2_25_proactive', paste0(country,"_", month,"_", "ps_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 15, 
       height = 17,
       bg = '#f7f7f7')

```

```{r import voyage ais data for Abidjan q2voyages, echo=F, include=F, warning=F}

start_date <- "'2025-01-01 00:00:00 UTC'"
end_date <- "'2025-07-01 00:00:00 UTC'"
voyages_table <- "`world-fishing-827.scratch_max.civ_q2_25_all_voyages_temp`"

# get list of carriers from TMT review
carrier_ssvids <- unique(filter(voyages_filtered, vessel_class == 'carrier')$MMSI)

# reformat to put into BQ
carrier_ssvids <-paste(paste0("'", carrier_ssvids, "'"), collapse = ", ")

# carrier_ssvids <- 
# 
# # potential MMSIs to force in 
# missing_ssvids <- '"311001159", "311001586", "312177000"'

  
voyages_ais_q <- readr::read_file(here::here("queries","proactive", "quarterly_carrier_ais.sql"))

voyage_ais <- fishwatchr::gfw_query(query = glue::glue(voyages_ais_q, 
                                    start_date = start_date,
                                    end_date = end_date,
                                    voyage_table = voyages_table, 
                                    carrier_ssvids = carrier_ssvids),
                                 run_query = TRUE,
                                 con = con)$data

```

```{r Make a voyage line plot map, echo=F, warning=F}

#set plot center to centre of IO
# new_center <- -15
new_center <- 2.5

# set proj for bounding box
# best_proj <- "+proj=eqearth +lon_0=-15 +wktext"
best_proj <- "+proj=eqearth +lon_0=2.5 +wktext"

# set plot limits for Atlantic 
# bounding_atlan <- transform_box(xlim = c(-70, 20),
#                           ylim = c(-55, 55),
#                           output_crs = best_proj)

bounding_atlan <- transform_box(xlim = c(-65, 20),
                          ylim = c(-55, 50),
                          output_crs = best_proj)

# rename voyage ais legend
voyage_ais$colour[voyage_ais$colour == 'port_profile'] <- 'q2_voyage'
#voyage_ais$colour[voyage_ais$colour == ''] <-
  
# make track into sf object 
voyage_ais_line <- voyage_ais %>%
  dplyr::select(trip_id,colour, timestamp, lat, lon) %>%
  sf::st_as_sf(., 
               coords = c("lon", "lat"), 
               crs = 4326) %>%
  group_by(trip_id, colour) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)

# make make   
q_carrier_map <- 
  ggplot() +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  geom_sf(data = voyage_ais_line, aes(colour=colour), alpha=0.2, linewidth = 1.5) +
  scale_colour_manual(values=rev(gfw_palettes[['primary']])) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bounding_atlan$box_out[['xmin']], bounding_atlan$box_out[['xmax']]),
           ylim = c(bounding_atlan$box_out[['ymin']], bounding_atlan$box_out[['ymax']]),
           crs = bounding_atlan$out_crs) 

# add globe# add globevalues()
q_carrier_map_glob <- fishwatchr::add_little_globe(q_carrier_map,
                             main_box = bounding_atlan,
                             globe_rel_size = 0.25,
                             globe_just = 'inside',
                             globe_position = 'upperright')  
  
# save object 
ggsave(q_carrier_map, 
       filename = here::here('outputs','figures','q2_25_proactive',
                             paste('CIV_q2_carrier_lines_highres_v',Sys.Date(),'.png', sep='')), 
       width = 8, 
       height = 10)

```


# Ghana 

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}
start_date <- "'2025-07-01 00:00:00 UTC'" 
end_date <- "'2025-09-30 23:59:59 UTC'"
year <- 2025

prev_visit_search_date <- "'2024-07-01 00:00:00 UTC'" 

country_iso3 <- "'GHA'"
# port_name <- "'ABIDJAN'"

# file names
month <- 'Q3'
country <- 'GHA'

# potential MMSIs to force in 
missing_ssvids <- '""'

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.gha_q3_25_all_voyages_temp`'
```

## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_v4.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    year = year,
                                                    missing_ssvids = missing_ssvids,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3),
                                 run_query = TRUE,
                                 con = con)

```
## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```
## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}
# import QA vessel list from TMT for identity corrections 
tmt_ves <- read.csv(here::here("data","TMT_qa_vessel_list", "Master_list_v3_Q3_2025.csv"), header=T) 

# reset ssvid to character
tmt_ves$ssvid <- as.character(tmt_ves$ssvid)

# Join update data to main data
merged_df <- left_join(voyages_with_coverage, tmt_ves, by = "ssvid", suffix = c("", "_tmt"))

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag_tmt",
  vessel_class_best  = "VesselType_tmt",
  geartype_best = "GearType_tmt"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}

# filter out the values from the master spreadsheet we shouldn't include
merged_df_inc <- filter(merged_df, Include == 'Yes' | is.na(Include))

# how many rows drop out
nrow(merged_df) - nrow(merged_df_inc)
```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df_inc, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df_inc$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df_inc$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df_inc$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```

## add port info
```{r add in port information for Ghana using anchorage stops}
# s2ids for port features of interest 
general_port <- c("102078b1", "102078bb", "102078a5", "102078a3", "102078bd", "10207899")
fuel <- c("102078bf")
fishing_port <- c("102078b7", "102078c7", "102078b9")
takoradi_gen <- c("0fe770a9", "0fe770a7", "0fe770a1", "0fe770a3", "0fe770a5", "0fe770af")

# add logic column to indicate presence at each location of interest 
voyages_url$tema_general <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% general_port)
})

voyages_url$tema_fuel <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% fuel)
})

voyages_url$tema_fishing <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% fishing_port)
})

voyages_url$takoradi_general <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% takoradi_gen)
})

```

## formatting
```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(voyages_url, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, at_dock=dock, tema_general, tema_fuel, tema_fishing, takoradi_general, num_fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter, num_encounters, loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url) #, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- ifelse(is.na(voyages_reformat$fishing_hs), FALSE, TRUE)

# write out data for initial TMT QA 
write.csv(voyages_reformat, here::here("data", "proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

```{r make adjustments from TMT feedback in GHA, echo=F, warning=F, include=FALSE}

# # manual addition of missing vessel
# extra <- data.frame(
#   vessel_name = "ORANGE FROST",
#   MMSI = "306883000",
#   Flag = "CUR",
#   AIS_Flag = "ANT",
#   imo = "9797656",
#   vessel_class_cat = "carrier",
#   vessel_class_confidence = "high",
#   vessel_class = "carrier",
#   vessel_type = "carrier",
#   previous_port_country = "AGO",
#   previous_port = "MATADI",
#   trip_start = as.POSIXct("2025-06-13 15:00:00", format = "%Y-%m-%d %H:%M:%S"),
#   trip_start_confidence = "1",
#   trip_end = as.POSIXct("2025-06-16 16:00:00", format = "%Y-%m-%d %H:%M:%S"),
#   trip_end_confidence = "1",
#   trip_duration_days = "0",
#   end_port = "ABIDJAN",
#   prev_visit_timestamp = as.POSIXct("2024-05-25 17:50:00", format = "%Y-%m-%d %H:%M:%S"),
#   at_dock = FALSE,
#   abj_lagoon = FALSE,
#   abj_vridi = FALSE,
#   abj_cargo = FALSE,
#   abj_fishing = FALSE,
#   abj_offshore = TRUE,
#   fishing = NA,
#   fishing_hours = FALSE,
#   fishing_eez = NA,
#   fishing_hs = FALSE,
#   fishing_rfmos = 0,
#   encounter = FALSE,
#   num_encounters = 0,
#   loitering = FALSE,
#   num_loitering = 0,    
#   AISdisabling =FALSE,
#   num_AISdisabling = NA, 
#   # Assuming this is the missing one
#   percent_ais_voyage = 100,    # Placeholder, adjust if needed
#   vv_url = ""
# )

#additions <- data.frame(rbind(voyages_reformat, extra))

# removals
exclude_mmsi <- c(636013068, 636013073, 636014240, 636014241, 657283600,
            412209163, 613003744, 636024729, 229705000, 563229800,
            563237900, 563245700, 311000876, 311000958, 374776000,
            247452100, 577030000)

# filter out removals
voyages_filtered <- voyages_reformat %>%
  filter(!MMSI %in% as.character(exclude_mmsi))

# make vessel type changes
# fishing 
fishing <- c(412800000)
voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(fishing)] <- 'fishing'
voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(fishing)] <- 'fishing'
voyages_filtered$Flag[voyages_filtered$MMSI %in% as.character(fishing)] <- 'unkwown'

# trawlers
trawl <- c(412209610)
voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(trawl)] <- 'trawler'
voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(trawl)] <- 'fishing'

# seiner 
sein <- c(312697000)
voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(sein)] <- 'tuna_purse_seines'

# name correction
voyages_filtered$vessel_name[voyages_filtered$MMSI %in% c(412330999)] <- 'LU YAN KAI YUAN YU 877'

# flag correction
voyages_filtered$Flag[voyages_filtered$MMSI %in% c(412209610)] <- 'CIV'

# carriers added 
carrier <- c(311001586, 311001159, 352351000)
voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(carrier)] <- 'carrier'
voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(carrier)] <- 'carrier'

tanker <- c(677028300)
voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(tanker)] <- 'tanker'
voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(tanker)] <- 'tanker'


# debugging code
# table(voyages_filtered$vessel_type)
# table(voyages_filtered$vessel_class)
# filter(voyages_filtered, vessel_type=='fishing')


write.csv(voyages_filtered, here::here("data", "proactive", "q2_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

```{r import voyage ais data for Ghana q2voyages, echo=F, include=F, warning=F}

start_date <- "'2025-01-01 00:00:00 UTC'"
end_date <- "'2025-07-01 00:00:00 UTC'"
voyages_table <- "`world-fishing-827.scratch_max.gha_q2_25_all_voyages_temp`"

# get list of carriers from TMT review
carrier_ssvids <- unique(filter(voyages_filtered, vessel_class == 'carrier')$MMSI)

# reformat to put into BQ
carrier_ssvids <-paste(paste0("'", carrier_ssvids, "'"), collapse = ", ")

# carrier_ssvids <- 
# 
# # potential MMSIs to force in 
# missing_ssvids <- '"311001159", "311001586", "312177000"'

  
voyages_ais_q <- readr::read_file(here::here("queries","proactive", "quarterly_carrier_ais.sql"))

voyage_ais <- fishwatchr::gfw_query(query = glue::glue(voyages_ais_q, 
                                    start_date = start_date,
                                    end_date = end_date,
                                    voyage_table = voyages_table, 
                                    carrier_ssvids = carrier_ssvids),
                                 run_query = TRUE,
                                 con = con)$data

```

```{r Make a gha voyage line plot map, echo=F, warning=F}

#set plot center to centre of IO
# new_center <- -15
new_center <- -15

# set proj for bounding box
# best_proj <- "+proj=eqearth +lon_0=-15 +wktext"
best_proj <- "+proj=eqearth +lon_0=-15 +wktext"

# set plot limits for Atlantic 
# bounding_atlan <- transform_box(xlim = c(-70, 20),
#                           ylim = c(-55, 55),
#                           output_crs = best_proj)

bounding_atlan <- transform_box(xlim = c(-30, 20),
                          ylim = c(-10, 35),
                          output_crs = best_proj)

# rename voyage ais legend
voyage_ais$colour[voyage_ais$colour == 'port_profile'] <- 'q2_voyage'
#voyage_ais$colour[voyage_ais$colour == ''] <-
  
# make track into sf object 
voyage_ais_line <- voyage_ais %>%
  dplyr::select(trip_id,colour, timestamp, lat, lon) %>%
  sf::st_as_sf(., 
               coords = c("lon", "lat"), 
               crs = 4326) %>%
  group_by(trip_id, colour) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)

# make make   
q_carrier_map <- 
  ggplot() +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  geom_sf(data = voyage_ais_line, aes(colour=colour), alpha=0.2, linewidth = 1.5) +
  scale_colour_manual(values=rev(gfw_palettes[['primary']])) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bounding_atlan$box_out[['xmin']], bounding_atlan$box_out[['xmax']]),
           ylim = c(bounding_atlan$box_out[['ymin']], bounding_atlan$box_out[['ymax']]),
           crs = bounding_atlan$out_crs) 

# add globe# add globevalues()
q_carrier_map_glob <- fishwatchr::add_little_globe(q_carrier_map,
                             main_box = bounding_atlan,
                             globe_rel_size = 0.25,
                             globe_just = 'inside',
                             globe_position = 'upperright')  
  
# save object 
ggsave(q_carrier_map_glob, 
       filename = here::here('outputs','figures','q2_25_proactive',
                             paste('GHA_q2_carrier_lines_highres_v',Sys.Date(),'.png', sep='')), 
       width = 8, 
       height = 10)

```


# Senegal  

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}
start_date <- "'2025-07-01 00:00:00 UTC'" 
end_date <- "'2025-09-30 23:59:59 UTC'"
year <- 2025

prev_visit_search_date <- "'2024-07-01 00:00:00 UTC'" 

country_iso3 <- "'SEN'"
# port_name <- "'DAKAR'"

# file names
month <- 'Q3'
country <- 'SEN'

# potential MMSIs to force in 
missing_ssvids <- '"209882000", "311000791", "355855000", "412440796", "416004904"'

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_max.sen_q3_25_all_voyages_temp`'

```

## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_v4.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    year = year,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    temp_table = temp_table_voyages,
                                                    missing_ssvids = missing_ssvids,
                                                    port_iso = country_iso3),
                                 run_query = TRUE,
                                 con = con)

```

## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```

## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}
# import QA vessel list from TMT for identity corrections 
sen_ves <- read.csv(here::here("data","TMT_qa_vessel_list", "Master_list_v3_Q3_2025.csv"), header=T) 

# reset ssvid to characher
sen_ves$ssvid <- as.character(sen_ves$ssvid)

# Join update data to main data
merged_df <- left_join(voyages_with_coverage, sen_ves, by = "ssvid", suffix = c("", "_tmt"))

#filter(merged_df, ssvid=='412209123')

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}
 

merged_df <- filter(merged_df, Include != 'No' | is.na(Include))

# filter out the values from the master spreadsheet we shouldn't include
#'merged_df_inc <- filter(merged_df, Include != 'Yes')

# how many rows drop out
# nrow(merged_df) - nrow(merged_df_inc)
```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```

## add port info
```{r add in port information for SEN using anchorage stops}
anchorages <- fishwatchr::gfw_query(query = c("SELECT s2id, lat, lon, label, sublabel FROM `world-fishing-827.anchorages.named_anchorages_v20240117` WHERE iso3 = 'SEN'"),
                       run_query = TRUE,
                       con = con)$data

table(anchorages$sublabel)

# s2ids for port features of interest 
container <- c("0ec173a9")
east_basin <- c("0ec173b1")
mid_basin <- c("0ec173b3")
west_basin <- c("0ec173ad")
entrance <- c("0ec173af")
navy <- c("0ec17253")
dak_fishing <- c("0ec17301", "0ec173ab", "0ec172ff", "0ec17255")

# large number of anchorages outside dakar - define with lat/lon box
dak_anchorage <- filter(anchorages, 
                        between(lat, 14.61, 14.72), 
                        between(lon, -17.42, -17.3))

dak_offshore <- dak_anchorage$s2id 


port_stops <- voyages_url %>%
  rowwise() %>%
  mutate(entrance = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% entrance),
         container = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% container),
         navy = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% navy),
         mid_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% mid_basin),
         east_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% east_basin),
         west_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% west_basin),
         dak_fishing = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% dak_fishing),
         dak_offshore = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% dak_offshore))

table(port_stops$dak_fishing)
```


```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(port_stops, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label,prev_visit_timestamp, entrance, navy, west_basin, mid_basin, east_basin, container, dak_fishing, dak_offshore, fishing = num_fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter, num_encounters, loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url) #, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- ifelse(is.na(voyages_reformat$fishing_hs), FALSE, TRUE)

# write out data for initial TMT QA 
write.csv(arrange(voyages_reformat, trip_end), here::here("data", "proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

```{r make adjustments from TMT feedback in GHA, echo=F, warning=F, include=FALSE}
# mis_ves_q3 <- read.csv(here::here("data", "proactive", "q3_2025",'TMT feedback - SEN - Q3 2025 - Missing vessels.csv'), header=T)
# 
# 
# mis_ves_q3$MMSI[!mis_ves_q3$MMSI %in% unique(voyages_reformat$MMSI)]

# manual addition of missing vessels from TMT cross check 
fegulus <- data.frame(
  vessel_name = "FEGULUS",
  MMSI = "311000644",
  Flag = "BHS",
  AIS_Flag = "BHS",
  imo = "9055709",
  vessel_class_cat = "carrier",
  vessel_class_confidence = "high",
  vessel_class = "carrier",
  vessel_type = "carrier",
  previous_port_country = "NLD",
  previous_port = "VLISSINGEN",
  trip_start = as.POSIXct("2024-08-28 19:10:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "4",
  trip_end = as.POSIXct("2025-09-04 17:21:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "4",
  trip_duration_days = "15",
  end_port = "DAKAR",
  prev_visit_timestamp = NA,
  entrance = FALSE,
  navy = FALSE,
  west_basin = FALSE,
  mid_basin = TRUE,
  east_basin = FALSE,
  container = FALSE,
  dak_fishing = FALSE,
  dak_offshore = TRUE,
  fishing = NA,
  fishing_hours = FALSE,
  fishing_eez = NA,
  fishing_hs = FALSE,
  fishing_rfmos = 0,
  encounter = FALSE,
  num_encounters = 0,
  loitering = FALSE,
  num_loitering = 0,
  AISdisabling =FALSE,
  num_AISdisabling = NA,
  # Assuming this is the missing one
  percent_ais_voyage = 100,    # Placeholder, adjust if needed
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public?latitude=14.962006446744125&longitude=-17.19591700382281&zoom=9.07680867070639&start=2025-08-26T00%3A00%3A00.000Z&end=2025-09-13T00%3A00%3A00.000Z&dvIn[0][id]=basemap&dvIn[0][cfg][basemap]=satellite&dvIn[1][id]=context-layer-high-seas&dvIn[1][cfg][vis]=false&dvIn[1][dvId]=high-seas&dvIn[2][id]=context-layer-mpa&dvIn[2][cfg][vis]=false&dvIn[2][dvId]=mpa&dvIn[3][id]=context-layer-rfmo&dvIn[3][cfg][vis]=false&dvIn[3][dvId]=tuna-rfmo-areas&dvIn[4][id]=context-layer-fao-areas&dvIn[4][cfg][vis]=false&dvIn[4][dvId]=fao-areas&dvIn[5][id]=context-layer-eez&dvIn[5][cfg][vis]=true&dvIn[5][dvId]=eez&dvIn[6][id]=context-layer-graticules&dvIn[6][cfg][vis]=false&dvIn[6][dvId]=graticules&dvIn[7][id]=vessel-6e068df88-8006-ba59-bfd0-b8ad1ac0fbe7&dvIn[7][dvId]=fishing-map-vessel-track-v-3&dvIn[7][cfg][track]=~1&dvIn[7][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[7][cfg][events][0]=~3&dvIn[7][cfg][events][1]=~4&dvIn[7][cfg][events][2]=~5&dvIn[7][cfg][events][3]=~6&dvIn[7][cfg][events][4]=~7&dvIn[7][cfg][rVIs][0]=783029bad-dc5a-cf78-c998-8897cf226a97&dvIn[7][cfg][rVIs][1]=232e60012-240b-d09b-3fd0-ae56fcd0ce4f&dvIn[7][cfg][clr]=%2333B679&dvIn[7][cfg][vis]=true&dvIn[7][dT]=false&dvIn[8][id]=vessel-689e79916-69d9-8c61-ac58-c321b6bc61e3&dvIn[8][dvId]=fishing-map-vessel-track-v-3&dvIn[8][cfg][track]=~1&dvIn[8][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[8][cfg][events][0]=~3&dvIn[8][cfg][events][1]=~4&dvIn[8][cfg][events][2]=~5&dvIn[8][cfg][events][3]=~6&dvIn[8][cfg][events][4]=~7&dvIn[8][cfg][rVIs][0]=1e56d3980-0915-2f1f-a3b4-c5e8488547ad&dvIn[8][cfg][rVIs][1]=288bb54a3-31ef-1072-0bf7-f8a131b854f9&dvIn[8][cfg][clr]=%23F95E5E&dvIn[8][dT]=false&dvIn[9][id]=ais&dvIn[9][cfg][vis]=false&dvIn[10][id]=vms&dvIn[10][cfg][vis]=false&bDV&lTD=&fTD=&tV=vessel&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=6e068df88-8006-ba59-bfd0-b8ad1ac0fbe7&vE[0]=loitering&vE[1]=encounter&vE[2]=port_visit&vS=areas&trackCorrectionId=&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0"
)

fyy7858 <- data.frame(
  vessel_name = "FU YUAN YU NO.7858",
  MMSI = "412440796",
  Flag = "CHN",
  AIS_Flag = "CHN",
  imo = "9921037",
  vessel_class_cat = "fishing",
  vessel_class_confidence = "high",
  vessel_class = "fishing",
  vessel_type = "drifting_longline",
  previous_port_country = "SEN",
  previous_port = "DAKAR",
  trip_start = as.POSIXct("2024-06-12 09:34:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "4",
  trip_end = as.POSIXct("2025-09-02 08:19:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "4",
  trip_duration_days = "82",
  end_port = "DAKAR",
  prev_visit_timestamp = as.POSIXct("2024-06-12 09:34:00", format = "%Y-%m-%d %H:%M:%S"),
  entrance = FALSE,
  navy = FALSE,
  west_basin = FALSE,
  mid_basin = FALSE,
  east_basin = FALSE,
  container = TRUE,
  dak_fishing = TRUE,
  dak_offshore = TRUE,
  fishing = TRUE,
  fishing_hours = 390,
  fishing_eez = NA,
  fishing_hs = TRUE,
  fishing_rfmos = 'ICCAT',
  encounter = FALSE,
  num_encounters = 0,
  loitering = FALSE,
  num_loitering = 0,
  AISdisabling =TRUE,
  num_AISdisabling = 2,
  # Assuming this is the missing one
  percent_ais_voyage = 48,    # Placeholder, adjust if needed
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public/vessel/2b3348d71-138e-ea60-d691-2e3e560e68d5?latitude=14.725195412451477&longitude=-17.283940637250033&zoom=10.07591326907632&start=2025-06-10T00%3A00%3A00.000Z&end=2025-09-05T00%3A00%3A00.000Z&dvIn[0][id]=vessel-2b3348d71-138e-ea60-d691-2e3e560e68d5&dvIn[0][dvId]=fishing-map-vessel-track-v-3&dvIn[0][cfg][track]=~1&dvIn[0][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[0][cfg][events][0]=~3&dvIn[0][cfg][events][1]=~4&dvIn[0][cfg][events][2]=~5&dvIn[0][cfg][events][3]=~6&dvIn[0][cfg][events][4]=~7&dvIn[0][cfg][rVIs][0]=e55037404-47c4-ca15-46ed-ac44d62f6ea3&dvIn[0][cfg][clr]=%23F95E5E&dvIn[0][cfg][vis]=true&dvIn[0][dT]=false&dvIn[1][id]=basemap&dvIn[1][cfg][basemap]=satellite&dvIn[2][id]=vessel-6e068df88-8006-ba59-bfd0-b8ad1ac0fbe7&dvIn[2][dvId]=fishing-map-vessel-track-v-3&dvIn[2][cfg][track]=~1&dvIn[2][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[2][cfg][events][0]=~3&dvIn[2][cfg][events][1]=~4&dvIn[2][cfg][events][2]=~5&dvIn[2][cfg][events][3]=~6&dvIn[2][cfg][events][4]=~7&dvIn[2][cfg][rVIs][0]=783029bad-dc5a-cf78-c998-8897cf226a97&dvIn[2][cfg][rVIs][1]=232e60012-240b-d09b-3fd0-ae56fcd0ce4f&dvIn[2][cfg][clr]=%2333B679&dvIn[2][cfg][vis]=false&dvIn[2][dT]=false&dvIn[3][id]=ais&dvIn[3][cfg][vis]=false&dvIn[4][id]=vms&dvIn[4][cfg][vis]=false&bDV&lTD=&fTD=&tV=vessel&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=2b3348d71-138e-ea60-d691-2e3e560e68d5&vE[0]=encounter&vE[1]=port_visit&vE[2]=fishing&vS=activity&trackCorrectionId=&vAm=voyage&vA=rfmo&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0"
)

mf1 <- data.frame(
  vessel_name = "MAAN FARN NO.1",
  MMSI = "416004904",
  Flag = "TWN",
  AIS_Flag = "TWN",
  imo = "9778284",
  vessel_class_cat = "fishing",
  vessel_class_confidence = "high",
  vessel_class = "fishing",
  vessel_type = "drifting_longline",
  previous_port_country = "ZAF",
  previous_port = "CAPE TOWN",
  trip_start = as.POSIXct("2024-05-03 07:55:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "4",
  trip_end = as.POSIXct("2025-08-24 06:48:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "4",
  trip_duration_days = "113",
  end_port = "DAKAR",
  prev_visit_timestamp = NA,
  entrance = FALSE,
  navy = FALSE,
  west_basin = FALSE,
  mid_basin = FALSE,
  east_basin = FALSE,
  container = FALSE,
  dak_fishing = TRUE,
  dak_offshore = TRUE,
  fishing = TRUE,
  fishing_hours = 1387,
  fishing_eez = NA,
  fishing_hs = TRUE,
  fishing_rfmos = 'ICCAT',
  encounter = TRUE,
  num_encounters = 2,
  loitering = FALSE,
  num_loitering = 0,
  AISdisabling =TRUE,
  num_AISdisabling = 2,
  percent_ais_voyage = 85,    
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public/vessel/3f9bee114-4cce-8e83-0d50-3b34aa6b2d37?latitude=-7.530544816329323&longitude=10.146738519540918&zoom=3.210656600190781&start=2025-05-01T00%3A00%3A00.000Z&end=2025-09-01T00%3A00%3A00.000Z&dvIn[0][id]=context-layer-high-seas&dvIn[0][cfg][vis]=false&dvIn[0][dvId]=high-seas&dvIn[1][id]=context-layer-mpa&dvIn[1][cfg][vis]=false&dvIn[1][dvId]=mpa&dvIn[2][id]=context-layer-rfmo&dvIn[2][cfg][vis]=false&dvIn[2][dvId]=tuna-rfmo-areas&dvIn[3][id]=context-layer-fao-areas&dvIn[3][cfg][vis]=false&dvIn[3][dvId]=fao-areas&dvIn[4][id]=context-layer-eez&dvIn[4][cfg][vis]=true&dvIn[4][dvId]=eez&dvIn[5][id]=context-layer-graticules&dvIn[5][cfg][vis]=false&dvIn[5][dvId]=graticules&dvIn[6][id]=vessel-3f9bee114-4cce-8e83-0d50-3b34aa6b2d37&dvIn[6][dvId]=fishing-map-vessel-track-v-3&dvIn[6][cfg][track]=~1&dvIn[6][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[6][cfg][events][0]=~3&dvIn[6][cfg][events][1]=~4&dvIn[6][cfg][events][2]=~5&dvIn[6][cfg][events][3]=~6&dvIn[6][cfg][events][4]=~7&dvIn[6][cfg][rVIs][0]=dc4940890-0883-9dd7-797b-ce8edfc33b2d&dvIn[6][cfg][rVIs][1]=b8ad97f4e-ef09-9c00-662c-6fdb99764e6f&dvIn[6][cfg][clr]=%23F09300&dvIn[6][cfg][vis]=true&dvIn[6][dT]=false&dvIn[7][id]=vessel-2b3348d71-138e-ea60-d691-2e3e560e68d5&dvIn[7][dvId]=fishing-map-vessel-track-v-3&dvIn[7][cfg][track]=~1&dvIn[7][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[7][cfg][events][0]=~3&dvIn[7][cfg][events][1]=~4&dvIn[7][cfg][events][2]=~5&dvIn[7][cfg][events][3]=~6&dvIn[7][cfg][events][4]=~7&dvIn[7][cfg][rVIs][0]=e55037404-47c4-ca15-46ed-ac44d62f6ea3&dvIn[7][cfg][clr]=%23F95E5E&dvIn[7][cfg][vis]=false&dvIn[7][dT]=false&dvIn[8][id]=basemap&dvIn[8][cfg][basemap]=satellite&dvIn[9][id]=vessel-6e068df88-8006-ba59-bfd0-b8ad1ac0fbe7&dvIn[9][dvId]=fishing-map-vessel-track-v-3&dvIn[9][cfg][track]=~1&dvIn[9][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[9][cfg][events][0]=~3&dvIn[9][cfg][events][1]=~4&dvIn[9][cfg][events][2]=~5&dvIn[9][cfg][events][3]=~6&dvIn[9][cfg][events][4]=~7&dvIn[9][cfg][rVIs][0]=783029bad-dc5a-cf78-c998-8897cf226a97&dvIn[9][cfg][rVIs][1]=232e60012-240b-d09b-3fd0-ae56fcd0ce4f&dvIn[9][cfg][clr]=%2333B679&dvIn[9][cfg][vis]=false&dvIn[9][dT]=false&dvIn[10][id]=ais&dvIn[10][cfg][vis]=false&dvIn[11][id]=vms&dvIn[11][cfg][vis]=false&bDV&lTD=&fTD=&tV=vessel&vDi=public-global-vessel-identity%3Av3.0&vIs=registryInfo&vSRi=3f9bee114-4cce-8e83-0d50-3b34aa6b2d37&vE[0]=encounter&vE[1]=port_visit&vE[2]=fishing&vS=areas&trackCorrectionId=&vAm=type&vA=eez&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0"
)

additions <- data.frame(rbind(voyages_reformat, fegulus, fyy7858, mf1))

# name correction
additions$vessel_name[additions$MMSI %in% c(412209172)] <- 'MENG XIN 22'
additions$vessel_name[additions$MMSI %in% c(412209178)] <- 'MENG XIN 27'
additions$vessel_name[additions$MMSI %in% c(629009232)] <- 'TWENTY'
additions$vessel_name[additions$MMSI %in% c(412331032)] <- 'LU QING YUAN YU 027'
additions$vessel_name[additions$MMSI %in% c(412420883)] <- 'MAME FARBA'
additions$vessel_name[additions$MMSI %in% c(412209083)] <- 'JU RONG YU 1'
additions$vessel_name[additions$MMSI %in% c(412420885)] <- 'SERIGNE SIDY NIANG'

# flag correction
additions$Flag[additions$MMSI %in% c(225995265, 224069140, 224175000)] <- 'ESP'
additions$Flag[additions$MMSI %in% c(412209009, 412209168, 412331133, 412549434, 412209011)] <- 'CHN'
additions$Flag[additions$MMSI %in% c(630124007)] <- 'GNB'
additions$Flag[additions$MMSI %in% c(412420883, 412420885)] <- 'SEN'

# debugging code
table(additions$vessel_type)
table(additions$vessel_class)
filter(additions, vessel_type=='unknown')
filter(additions, vessel_class=='Reefer containership')


# vessel_class corrections  
additions$vessel_class[additions$MMSI %in% c(440257000)] <- 'carrier'
additions$vessel_class[additions$MMSI %in% c(629100000)] <- 'fishing'

# carrier <- c(311001586, 311001159, 352351000)
# voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(carrier)] <- 'carrier'
# voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(carrier)] <- 'carrier'
# 
# # add seiners 
# seiner <- c(312078000, 312360000, 312360000)
# voyages_filtered$vessel_type[voyages_filtered$MMSI %in% as.character(seiner)] <- 'tuna_purse_seines'
# voyages_filtered$vessel_class[voyages_filtered$MMSI %in% as.character(seiner)] <- 'fishing'



write.csv(additions, here::here("data", "proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)
```

```{r SEN pull in the fishing data, echo=F, warning=F, include=FALSE}

q_confidence <- readr::read_file(here::here("queries","proactive", "proactive_fishing_locations.sql"))

fishing <- fishwatchr::gfw_query(query = glue::glue(q_confidence,
                                               voyages_table = "`world-fishing-827.scratch_joef.sen_q2_25_all_voyages_temp`" 
                                               ),
                                 run_query = TRUE,
                                 con = con)$data

# sense check the data 
fishing %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

# add gear from TMT review 
gear <- distinct(dplyr::select(voyages_filtered, MMSI, Flag, vessel_type)) %>% 
  mutate(ssvid=as.character(MMSI))

fishing_data <- left_join(fishing, gear, by = join_by(ssvid))


```

```{r SEN voyage activity longline maps, echo=F, warning=F, include=FALSE}

# bin the data
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.5)*0.5
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.5)*0.5

table(fishing_data$vessel_type)

# count positions in each lat lon bin
longline_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data, vessel_type %in% c('drifting_longlines')) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 500 
#set plot center 
new_center <- 40

# 
quantile(longline_raster$fishing_hours)

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-45, 0),
                          ylim = c(15, -15),
                          output_crs = best_proj)

# map for atlantic longline 
atl_full <- longline_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(atl_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q2_25_proactive', paste0(country,"_", month,"_", "longline_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 15, 
       height = 17,
       bg = '#f7f7f7')

```


```{r SEN voyage activity trawl maps, echo=F, warning=F, include=FALSE}
# add a different lat lon bin 
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.1)*0.1
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.1)*0.1


# count positions in each lat lon bin
trawl_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data, vessel_type %in% c('trawlers')) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 9000 
#set plot center 
new_center <- 17

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=17 +wktext"

# set plot limits bound on the data
bounding_wa <- transform_box(xlim = c(-20, -14),
                          ylim = c(16, 8.5),
                          output_crs = best_proj)

# trawl map 
trawl_full <- trawl_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                       limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_wa$box_out[['xmin']], bounding_wa$box_out[['xmax']]),
      ylim = c(bounding_wa$box_out[['ymin']], bounding_wa$box_out[['ymax']]),
      crs = bounding_wa$out_crs) +
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light')  +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(trawl_full,
                             main_box = bounding_wa,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures', 'q2_25_proactive', paste0(country,"_", month,"_", "trawl_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 15, 
       height = 17,
       bg = '#f7f7f7')

```



# Kenya  

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}
# start_date <- "'2025-04-01 00:00:00 UTC'" 
# end_date <- "'2025-06-30 23:59:59 UTC'"
# year <- 2025
# 
# prev_visit_search_date <- "'2022-01-01 00:00:00 UTC'" 

country_iso3 <- "'KEN'"
#port_name <- "'MOMBASA'"

# file names
month <- 'Q3'
country <- 'KEN'

missing_ssvids <- '"500008222", "500008222"'

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_max.ken_q3_25_all_voyages_temp`'
```

```{r voyages all, echo=F, warning=F, include=FALSE}

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_v4.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    year = year,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3),
                                 run_query = TRUE,
                                 con = con)

```

```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```

```{r gear type corrections for Kenya from TMT data, echo=F, warning=F, include=FALSE}
# import QA vessel list from TMT for identity corrections 
master_list <- read.csv(here::here("data","TMT_qa_vessel_list", "Master_list_v3_Q3_2025.csv"), header=T) 

# reset ssvid to characher
master_list$ssvid <- as.character(master_list$ssvid)

# Join update data to main data
merged_df <- left_join(voyages_with_coverage, master_list, by = "ssvid", suffix = c("", "_tmt"))

#filter(merged_df, ssvid=='412209123')

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}

table(merged_df$Include)

#merged_df <- filter(merged_df, Include != 'No')

```


```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```



```{r add in port information for SEN using anchorage stops}
anchorages <- fishwatchr::gfw_query(query = c("SELECT s2id, lat, lon, label, sublabel FROM `world-fishing-827.anchorages.named_anchorages_v20240117` WHERE iso3 = 'KEN'"),
                       run_query = TRUE,
                       con = con)$data

table(anchorages$sublabel)

# write.csv(anchorages, here::here("data","2025_q1", paste(country,'anchorages-', Sys.Date(),".csv", sep='')), row.names=F)


# s2ids for port features of interest 
general <- c("18401349", "18401347",  "18406d2b", "18406d31", 
             "18406d13", "18406d6b", "18406d15", "18406d2d", "18406d41", "18406d47", 
             "18406d37", "18406d33", "18406d49", "18406d0d")
fishing <- c("18401331", "1840132d")
dry_dock <- c("18401337","18401339")
fish_harbour <- c("18406cd3", "18406ccd" , "18406ccf",  "18406cd1")
harbor <- c("18406d0f", "18406da9", "18406d07", "18406daf", "18406d09", "18406da7",
            "18406cd7", "18406d2f", "18406d29")


port_stops <- voyages_url %>%
  rowwise() %>%
  mutate(mom_general = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% general),
         mom_fishing = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% fishing),
         mom_fishing_harbor = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% fish_harbour),
         mom_drydock = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% dry_dock),
         mom_harbor = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% harbor))

```


```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(port_stops, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, mom_general, mom_fishing, mom_fishing_harbor, mom_harbor, mom_drydock,  fishing=num_fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter= encounter, num_encounters=num_encounters, loitering=loitering, num_loitering, AISdisabling,            num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url)
   #gaps=1, num_gaps, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- ifelse(is.na(voyages_reformat$fishing_hs), FALSE, TRUE)

write.csv(voyages_reformat, here::here("data","proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

```{r edits based on TMT feedback, echo=F, warning=F, include=FALSE}
# removals
exclude_mmsi <- c(257384000, 259023000, 257248000, 636019515, 677084900, 511100417)

# filter out removals
voyages_filtered <- voyages_reformat %>%
  filter(!MMSI %in% as.character(exclude_mmsi))

# update flag when not correct on AIS 
voyages_filtered$Flag[voyages_filtered$MMSI %in% c(457900757)] <- 'KEN'

am1 <- data.frame(
  vessel_name = "AL MARWAN 1",
  MMSI = "417102231",
  Flag = "SRI",
  #AIS_Flag = "SRI",
  imo = NA,
  vessel_class_cat = NA,
  vessel_class_confidence = NA,
  vessel_class = NA,
  vessel_type = NA,
  previous_port_country = NA,
  previous_port = NA,
  trip_start = NA,
  trip_start_confidence = NA,
  trip_end = as.POSIXct("2025-08-18 03:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "2",
  trip_duration_days = NA,
  end_port = "LAMU",
  prev_visit_timestamp = NA,
  mom_general = FALSE,
  mom_fishing = FALSE,
  mom_fishing_harbor = FALSE,
  mom_harbor = FALSE,
  mom_drydock = FALSE,
  fishing = NA,
  fishing_hours = NA,
  fishing_eez = NA,
  fishing_hs = NA,
  fishing_rfmos = NA,
  encounter = NA,
  num_encounters = NA,
  loitering = NA,
  num_loitering = NA,
  AISdisabling = TRUE,
  num_AISdisabling = NA,
  # Assuming this is the missing one
  percent_ais_voyage = 5,    # Placeholder, adjust if needed
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public/vessel/e2ef50ea0-0659-430a-4cd7-08a279f217be?dvIn[0][id]=vessel-e2ef50ea0-0659-430a-4cd7-08a279f217be&dvIn[0][dvId]=fishing-map-vessel-track-v-3&dvIn[0][cfg][track]=~1&dvIn[0][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[0][cfg][events][0]=~3&dvIn[0][cfg][events][1]=~4&dvIn[0][cfg][events][2]=~5&dvIn[0][cfg][events][3]=~6&dvIn[0][cfg][events][4]=~7&dvIn[0][cfg][clr]=%23F09300&dvIn[0][cfg][vis]=true&dvIn[0][dT]=false&dvIn[1][id]=ais&dvIn[1][cfg][vis]=false&dvIn[2][id]=vms&dvIn[2][cfg][vis]=false&dvIn[3][id]=vessel-1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&dvIn[3][dvId]=fishing-map-vessel-track-v-3&dvIn[3][cfg][track]=~1&dvIn[3][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[3][cfg][events][0]=~3&dvIn[3][cfg][events][1]=~4&dvIn[3][cfg][events][2]=~5&dvIn[3][cfg][events][3]=~6&dvIn[3][cfg][events][4]=~7&dvIn[3][cfg][clr]=%2333B679&dvIn[3][dT]=false&dvIn[4][id]=vessel-ca93d9cb6-629f-2a40-6083-b49a6bd3cd7d&dvIn[4][dvId]=fishing-map-vessel-track-v-3&dvIn[4][cfg][clr]=%23F95E5E&dvIn[4][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[4][cfg][track]=~1&dvIn[4][cfg][events][0]=~3&dvIn[4][cfg][events][1]=~4&dvIn[4][cfg][events][2]=~5&dvIn[4][cfg][events][3]=~6&dvIn[4][cfg][events][4]=~7&dvIn[4][cfg][rVIs][0]=02998712f-ffa6-d93d-1fd8-22b50ce4d5e2&dvIn[4][cfg][rVIs][1]=08259edfb-b2f8-a671-4f24-0fed53f228e5&dvIn[4][cfg][vis]=false&dvIn[4][dT]=false&longitude=41.26847594185102&latitude=-1.1282657478810505&zoom=6.9901521135821305&lTD=&fTD=&tV=vessel&bDV&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=e2ef50ea0-0659-430a-4cd7-08a279f217be&vE[0]=loitering&vE[1]=encounter&vE[2]=port_visit&trackCorrectionId=&start=2025-08-17T22%3A00%3A00.000Z&end=2025-08-19T00%3A00%3A00.000Z"
)

t_1 <- data.frame(
  vessel_name = "T",
  MMSI = "500008222",
  Flag = "unknown",
  #AIS_Flag = "unknown",
  imo = NA,
  vessel_class_cat = "fishing",
  vessel_class_confidence = "low",
  vessel_class = "fishing",
  vessel_type = "unknown",
  previous_port_country = "KEN",
  previous_port = "LAMU",
  trip_start = as.POSIXct("2025-07-04 08:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "3",
  trip_end = as.POSIXct("2025-07-12 06:48:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "3",
  trip_duration_days = "7",
  end_port = "LAMU",
  prev_visit_timestamp = as.POSIXct("2025-06-26 09:30:00", format = "%Y-%m-%d %H:%M:%S"),
  mom_general = FALSE,
  mom_fishing = FALSE,
  mom_fishing_harbor = FALSE,
  mom_harbor = FALSE,
  mom_drydock = FALSE,
  fishing = TRUE,
  fishing_hours = NA,
  fishing_eez = 'SOM',
  fishing_hs = TRUE,
  fishing_rfmos = NA,
  encounter = NA,
  num_encounters = NA,
  loitering = NA,
  num_loitering = NA,
  AISdisabling = NA,
  num_AISdisabling = NA,
  percent_ais_voyage = NA,    
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public?dvIn[0][id]=context-layer-eez&dvIn[0][cfg][vis]=true&dvIn[1][id]=basemap&dvIn[1][cfg][basemap]=satellite&dvIn[2][id]=vessel-e2ef50ea0-0659-430a-4cd7-08a279f217be&dvIn[2][dvId]=fishing-map-vessel-track-v-3&dvIn[2][cfg][track]=~1&dvIn[2][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[2][cfg][events][0]=~3&dvIn[2][cfg][events][1]=~4&dvIn[2][cfg][events][2]=~5&dvIn[2][cfg][events][3]=~6&dvIn[2][cfg][events][4]=~7&dvIn[2][cfg][clr]=%23F09300&dvIn[2][cfg][vis]=true&dvIn[2][dT]=false&dvIn[3][id]=ais&dvIn[3][cfg][vis]=false&dvIn[4][id]=vms&dvIn[4][cfg][vis]=false&dvIn[5][id]=vessel-1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&dvIn[5][dvId]=fishing-map-vessel-track-v-3&dvIn[5][cfg][track]=~1&dvIn[5][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[5][cfg][events][0]=~3&dvIn[5][cfg][events][1]=~4&dvIn[5][cfg][events][2]=~5&dvIn[5][cfg][events][3]=~6&dvIn[5][cfg][events][4]=~7&dvIn[5][cfg][clr]=%2333B679&dvIn[5][cfg][vis]=true&dvIn[5][dT]=false&dvIn[6][id]=vessel-ca93d9cb6-629f-2a40-6083-b49a6bd3cd7d&dvIn[6][dvId]=fishing-map-vessel-track-v-3&dvIn[6][cfg][clr]=%23F95E5E&dvIn[6][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[6][cfg][track]=~1&dvIn[6][cfg][events][0]=~3&dvIn[6][cfg][events][1]=~4&dvIn[6][cfg][events][2]=~5&dvIn[6][cfg][events][3]=~6&dvIn[6][cfg][events][4]=~7&dvIn[6][cfg][rVIs][0]=02998712f-ffa6-d93d-1fd8-22b50ce4d5e2&dvIn[6][cfg][rVIs][1]=08259edfb-b2f8-a671-4f24-0fed53f228e5&dvIn[6][cfg][vis]=false&dvIn[6][dT]=false&longitude=41.106662306179096&latitude=-2.127950101465794&zoom=9.458787220968267&lTD=&fTD=&tV=vessel&bDV&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&vE[0]=encounter&vE[1]=port_visit&trackCorrectionId=&start=2025-07-05T00%3A00%3A00.000Z&end=2025-07-13T00%3A00%3A00.000Z"
)


t_2 <- data.frame(
  vessel_name = "T",
  MMSI = "500008222",
  Flag = "unknown",
  #AIS_Flag = "unknown",
  imo = NA,
  vessel_class_cat = "fishing",
  vessel_class_confidence = "low",
  vessel_class = "fishing",
  vessel_type = "unknown",
  previous_port_country = "KEN",
  previous_port = "LAMU",
  trip_start = as.POSIXct("2025-08-01 05:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "3",
  trip_end = as.POSIXct("2025-08-08 22:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "3",
  trip_duration_days = "6",
  end_port = "LAMU",
  prev_visit_timestamp = as.POSIXct("2025-07-12 06:48:00", format = "%Y-%m-%d %H:%M:%S"),
  mom_general = FALSE,
  mom_fishing = FALSE,
  mom_fishing_harbor = FALSE,
  mom_harbor = FALSE,
  mom_drydock = FALSE,
  fishing = TRUE,
  fishing_hours = 83,
  fishing_eez = 'SOM',
  fishing_hs = TRUE,
  fishing_rfmos = NA,
  encounter = NA,
  num_encounters = NA,
  loitering = NA,
  num_loitering = NA,
  AISdisabling = NA,
  num_AISdisabling = NA,
  percent_ais_voyage = NA,    
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public/vessel/1c3dd9ed8-87b8-557c-e9e1-c22886f9d767?dvIn[0][id]=basemap&dvIn[0][cfg][basemap]=satellite&dvIn[1][id]=vessel-e2ef50ea0-0659-430a-4cd7-08a279f217be&dvIn[1][dvId]=fishing-map-vessel-track-v-3&dvIn[1][cfg][track]=~1&dvIn[1][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[1][cfg][events][0]=~3&dvIn[1][cfg][events][1]=~4&dvIn[1][cfg][events][2]=~5&dvIn[1][cfg][events][3]=~6&dvIn[1][cfg][events][4]=~7&dvIn[1][cfg][clr]=%23F09300&dvIn[1][cfg][vis]=true&dvIn[1][dT]=false&dvIn[2][id]=ais&dvIn[2][cfg][vis]=false&dvIn[3][id]=vms&dvIn[3][cfg][vis]=false&dvIn[4][id]=vessel-1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&dvIn[4][dvId]=fishing-map-vessel-track-v-3&dvIn[4][cfg][track]=~1&dvIn[4][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[4][cfg][events][0]=~3&dvIn[4][cfg][events][1]=~4&dvIn[4][cfg][events][2]=~5&dvIn[4][cfg][events][3]=~6&dvIn[4][cfg][events][4]=~7&dvIn[4][cfg][clr]=%2333B679&dvIn[4][cfg][vis]=true&dvIn[4][dT]=false&dvIn[5][id]=vessel-ca93d9cb6-629f-2a40-6083-b49a6bd3cd7d&dvIn[5][dvId]=fishing-map-vessel-track-v-3&dvIn[5][cfg][clr]=%23F95E5E&dvIn[5][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[5][cfg][track]=~1&dvIn[5][cfg][events][0]=~3&dvIn[5][cfg][events][1]=~4&dvIn[5][cfg][events][2]=~5&dvIn[5][cfg][events][3]=~6&dvIn[5][cfg][events][4]=~7&dvIn[5][cfg][rVIs][0]=02998712f-ffa6-d93d-1fd8-22b50ce4d5e2&dvIn[5][cfg][rVIs][1]=08259edfb-b2f8-a671-4f24-0fed53f228e5&dvIn[5][cfg][vis]=false&dvIn[5][dT]=false&longitude=42.01295905799963&latitude=-1.257907291364283&zoom=7.471396945017982&lTD=&fTD=&tV=vessel&bDV&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&vE[0]=encounter&vE[1]=port_visit&vE[2]=fishing&trackCorrectionId=&start=2025-07-31T00%3A00%3A00.000Z&end=2025-08-10T00%3A00%3A00.000Z&vS=activity"
)

t_3 <- data.frame(
  vessel_name = "T",
  MMSI = "500008222",
  Flag = "unknown",
  #AIS_Flag = "unknown",
  imo = NA,
  vessel_class_cat = "fishing",
  vessel_class_confidence = "low",
  vessel_class = "fishing",
  vessel_type = "unknown",
  previous_port_country = "KEN",
  previous_port = "LAMU",
  trip_start = as.POSIXct("2025-08-14 15:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_start_confidence = "3",
  trip_end = as.POSIXct("2025-08-21 12:00:00", format = "%Y-%m-%d %H:%M:%S"),
  trip_end_confidence = "3",
  trip_duration_days = "7",
  end_port = "LAMU",
  prev_visit_timestamp = as.POSIXct("2025-08-08 22:00:00", format = "%Y-%m-%d %H:%M:%S"),
  mom_general = FALSE,
  mom_fishing = FALSE,
  mom_fishing_harbor = FALSE,
  mom_harbor = FALSE,
  mom_drydock = FALSE,
  fishing = TRUE,
  fishing_hours = NA,
  fishing_eez = 'SOM',
  fishing_hs = TRUE,
  fishing_rfmos = NA,
  encounter = NA,
  num_encounters = NA,
  loitering = NA,
  num_loitering = NA,
  AISdisabling = NA,
  num_AISdisabling = NA,
  percent_ais_voyage = NA,    
  vv_url = "https://globalfishingwatch.org/map/fishing-activity/default-public/vessel/1c3dd9ed8-87b8-557c-e9e1-c22886f9d767?dvIn[0][id]=basemap&dvIn[0][cfg][basemap]=satellite&dvIn[1][id]=vessel-e2ef50ea0-0659-430a-4cd7-08a279f217be&dvIn[1][dvId]=fishing-map-vessel-track-v-3&dvIn[1][cfg][track]=~1&dvIn[1][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[1][cfg][events][0]=~3&dvIn[1][cfg][events][1]=~4&dvIn[1][cfg][events][2]=~5&dvIn[1][cfg][events][3]=~6&dvIn[1][cfg][events][4]=~7&dvIn[1][cfg][clr]=%23F09300&dvIn[1][cfg][vis]=true&dvIn[1][dT]=false&dvIn[2][id]=ais&dvIn[2][cfg][vis]=false&dvIn[3][id]=vms&dvIn[3][cfg][vis]=false&dvIn[4][id]=vessel-1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&dvIn[4][dvId]=fishing-map-vessel-track-v-3&dvIn[4][cfg][track]=~1&dvIn[4][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[4][cfg][events][0]=~3&dvIn[4][cfg][events][1]=~4&dvIn[4][cfg][events][2]=~5&dvIn[4][cfg][events][3]=~6&dvIn[4][cfg][events][4]=~7&dvIn[4][cfg][clr]=%2333B679&dvIn[4][cfg][vis]=true&dvIn[4][dT]=false&dvIn[5][id]=vessel-ca93d9cb6-629f-2a40-6083-b49a6bd3cd7d&dvIn[5][dvId]=fishing-map-vessel-track-v-3&dvIn[5][cfg][clr]=%23F95E5E&dvIn[5][cfg][info]=public-global-vessel-identity%3Av3.0&dvIn[5][cfg][track]=~1&dvIn[5][cfg][events][0]=~3&dvIn[5][cfg][events][1]=~4&dvIn[5][cfg][events][2]=~5&dvIn[5][cfg][events][3]=~6&dvIn[5][cfg][events][4]=~7&dvIn[5][cfg][rVIs][0]=02998712f-ffa6-d93d-1fd8-22b50ce4d5e2&dvIn[5][cfg][rVIs][1]=08259edfb-b2f8-a671-4f24-0fed53f228e5&dvIn[5][cfg][vis]=false&dvIn[5][dT]=false&longitude=41.28790725047901&latitude=-1.7015996318399558&zoom=7.471396945017982&lTD=&fTD=&tV=vessel&bDV&tk[0]=fishing-map-vessel-track-v-3&tk[1]=public-global-all-tracks%3Av3.0&tk[2]=public-global-vessel-identity%3Av3.0&tk[3]=public-global-fishing-events%3Av3.0&tk[4]=public-global-port-visits-events%3Av3.1&tk[5]=public-global-encounters-events%3Av3.0&tk[6]=public-global-loitering-events%3Av3.0&tk[7]=public-global-gaps-events%3Av3.0&vDi=public-global-vessel-identity%3Av3.0&vIs=selfReportedInfo&vSRi=1c3dd9ed8-87b8-557c-e9e1-c22886f9d767&vE[0]=encounter&vE[1]=port_visit&trackCorrectionId=&start=2025-08-13T00%3A00%3A00.000Z&end=2025-08-25T00%3A00%3A00.000Z&vS=insights"
)

additions <- data.frame(rbind(voyages_filtered, am1, t_1, t_2, t_3))


write.csv(additions, here::here("data","proactive", "q3_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)
```
