---
title: "Port_Program_Quarterly_Q4_2025 (and Jan 2026)"
author: "Max Schofield and joe F"
date: "2026-02"
output: html_document
---

```{=html}
<style>
body {
text-align: left}
</style>
```

# Setup 

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, echo=F, warning=F, include=FALSE}
load_or_install_libraries <- function(x){
  for( i in x ){
    #  require returns TRUE invisibly if it was able to load package
    if( ! require( i , character.only = TRUE ) ){
      #  If package was not able to be loaded then re-install
      install.packages( i , dependencies = TRUE )
      #  Load package after installing
      require( i , character.only = TRUE )
    }
  }
}

#  Then try/install packages...
load_or_install_libraries( c("tidyverse" , "bigrquery" ,"devtools", "DBI","glue", "lubridate", "here", "sf", "extrafont", "patchwork", "terra", "rgeos", "ggspatial", "ggrepel", "tibble", "purrr", "stringr") )

# get fishwatch r independently 
if (!require("fishwatchr")) {devtools::install_github("GlobalFishingWatch/fishwatchr")}
library(fishwatchr)
```

```{r connection to BQ, echo=F, warning=F, include=FALSE}
con <- DBI::dbConnect(drv = bigrquery::bigquery(), 
                      project = "world-fishing-827", 
                      use_legacy_sql = FALSE)
```

## Set global parameters
```{r}

start_date <- "'2025-10-01 00:00:00 UTC'" 
end_date <- "'2026-01-31 23:59:59 UTC'"
start_year <- 2025 ## 
end_year <- 2026 ## 
year <- 2025

# # when to look for previous visits
prev_visit_search_date <- "'2024-10-01 00:00:00 UTC'" 

# import QA vessel list from TMT for including potentially missed vessels
tmt_masterlist <- read.csv(here::here("data","TMT_qa_vessel_list", "Master_list_v5_march2026.csv"), header=T) 
ssvid_master_include <- tmt_masterlist %>% filter(Include == "Yes") %>% pull(ssvid) %>% as.character(.)
        
```

## Manual voyage add function
```{r}
## function to map R dataframe to CTE format
manual_voyage_fxn <- function(df, cte_name = "manual_voyage_data") {
  
  # 1. Format the data values for the SQL string
  formatted_df <- df %>%
    dplyr::mutate(
      # Timestamps: trip_start / trip_end get the TIMESTAMP('...') wrapper
      across(any_of(c("trip_start", "trip_end")), 
             ~ ifelse(is.na(.x), "NULL", paste0("TIMESTAMP('", as.character(.x), "')"))),
      
      # Integers/Numbers: NO quotes. 
      # We explicitly include the confidence columns here just in case they are characters in R
      across(where(is.numeric) | any_of(c("year", "trip_start_confidence", "trip_end_confidence")), 
             ~ ifelse(is.na(.x), "NULL", as.character(.x))),
      
      # Strings: Wrap in single quotes
      # We exclude the timestamps AND the confidence columns so they don't get quotes
      across(where(is.character) & !any_of(c("year", "trip_start", "trip_end", "trip_start_confidence", "trip_end_confidence")), 
             ~ ifelse(is.na(.x), "NULL", paste0("'", .x, "'")))
    )

  # 2. Build the rows: (val1, val2, ...)
  rows <- apply(formatted_df, 1, function(x) paste0("(", paste(x, collapse = ", "), ")"))
  all_rows <- paste(rows, collapse = ",\n    ")
  
  # 3. Define the Schema for the STRUCT (Crucial for BQ Type Casting)
  col_names <- colnames(df)
  schema_definition <- purrr::map_chr(col_names, ~ {
    if (.x %in% c("trip_start", "trip_end")) return(paste(.x, "TIMESTAMP"))
    if (.x %in% c("year", "trip_start_confidence", "trip_end_confidence")) return(paste(.x, "INT64"))
    return(paste(.x, "STRING"))
  }) %>% paste(collapse = ", ")

  # 4. Wrap it in the CTE syntax
  glue::glue("
    {cte_name} AS (
      SELECT * FROM UNNEST([
        STRUCT<{schema_definition}>
        {all_rows}
      ])
    )")
}

```

# Cote Divore

## set parameters for analysis 
```{r set date and port parameters, echo=F, warning=F, include=FALSE}

country_iso3 <- "'CIV'"
# port_name <- "'ABIDJAN'"

# file names
month <- 'Q4'
country <- 'CIV'

# additional MMSIs to force in
missing_ssvids_manual <- c('')

missing_ssvids <- c(missing_ssvids_manual, ssvid_master_include) %>% paste0("'", ., "'", collapse = ", ")

```
## add manual voyages if needed
```{r}

### add manual voyage and vessel details
# RUNAWAY BAY
row1 <- data.frame(
  year = 2025,
  ssvid = "311001116",
  vessel_id = "8e54128eb-bb4b-3ce1-5379-f529529cb837",
  vessel_iso3 = "BHS",
  class_confidence = "1",
  vessel_class = "Carrier vessel",
  gear_type = "",
  trip_id = "manual_add_1",
  trip_start = as.POSIXct("2025-09-27 17:17:50", tz = "UTC"),
  trip_end = as.POSIXct("2025-10-08 08:11:21", tz = "UTC"),
  trip_start_anchorage_id = "47db6389",
  trip_end_anchorage_id = "0fc1e631",
  trip_start_visit_id = "aa90dbfef2aba6ff393cf12a2cd27721",
  trip_end_visit_id = "5229768d6fc7adc63bff5fde7452868d",
  trip_start_confidence = 1,
  trip_end_confidence = 1,
  start_label = "ANTWERP",
  start_iso3 = "BEL",
  end_label = "ABIDJAN",
  end_iso3 = "CIV",
    stringsAsFactors = FALSE
)

# ATLANTIC QUEEN - fully manual (no visit in GFW data, only approaches far outer reaches of offshore anchs)
row2 <- data.frame(
  year = 2025,
  ssvid = "627179000",
  vessel_id = "3f7c46fe4-45f8-0685-a7e5-60d531c7c352",
  vessel_iso3 = "GHA",
  class_confidence = "1",
  vessel_class = "Fishing vessel",
  gear_type = "tuna_purse_seines",
  trip_id = "manual_add_2",
  trip_start = as.POSIXct("2025-12-11 09:31:21", tz = "UTC"),
  trip_end = as.POSIXct("2026-01-13 07:37:00", tz = "UTC"), ## estimated from map
  trip_start_anchorage_id = "102070ab",
  trip_end_anchorage_id = "NA",
  trip_start_visit_id = "988bd9df4f9aa5e2a74b7a902c624df0",
  trip_end_visit_id = "NA",
  trip_start_confidence = 4,
  trip_end_confidence = 1,
  start_label = "TEMA",
  start_iso3 = "GHA",
  end_label = "ABIDJAN",
  end_iso3 = "CIV",
    stringsAsFactors = FALSE
)

# LU QING YUAN YU 028 - bad voyages bc duplicate ids - need to delete extra after running
row3 <- data.frame(
  year = 2025,
  ssvid = "412331033",
  vessel_id = "e44610c28-8936-0ab8-e62b-0d27b5af60a7",
  vessel_iso3 = "CHN",
  class_confidence = "1",
  vessel_class = "Fishing vessel",
  gear_type = "drifting_longlines",
  trip_id = "manual_add_3",
  trip_start = as.POSIXct("2025-11-07 16:11:24", tz = "UTC"),
  trip_end = as.POSIXct("2025-11-24 16:11:42", tz = "UTC"), ## estimated from map
  trip_start_anchorage_id = "0f04c3f3",
  trip_end_anchorage_id = "0fc1ef6b",
  trip_start_visit_id = "a8c3a96270d196a06b13823e200938dc",
  trip_end_visit_id = "aca692a13ce695f7741532f76a556eba",
  trip_start_confidence = 4,
  trip_end_confidence = 4,
  start_label = "FREETOWN",
  start_iso3 = "SLE",
  end_label = "PORT BOUET ANCHORAGE",
  end_iso3 = "CIV",
    stringsAsFactors = FALSE
)

missing_voyages_df <- bind_rows(row1, row2, row3)

# Convert to SQL string
manual_voyage_cte <- manual_voyage_fxn(missing_voyages_df, cte_name = "manual_voyage_data")

```


## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.civ_q4_25_all_voyages_temp`'

# load query
voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_q4_2025.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    missing_ssvids = missing_ssvids,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3,
                                                    prev_visit_search_date = prev_visit_search_date),
                                                    manual_voyage_cte = manual_voyage_cte, # manual voyage 
                                 run_query = TRUE,
                                 con = con)

```

## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```

## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}

# use QA master vessel list from TMT for identity corrections 
# tmt_masterlist

# reset ssvid to character
tmt_masterlist$ssvid <- as.character(tmt_masterlist$ssvid)

# Join update data to main data - CHECK to make sure no duplicates
merged_df <- left_join(voyages_with_coverage, tmt_masterlist, by = "ssvid", suffix = c("", "_tmt"))

#filter(merged_df, ssvid=='412209123')

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  # shipname = "CurrentName",
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}

# filter out the values from the master spreadsheet we shouldn't include
merged_df <- filter(merged_df, Include == 'Yes' | is.na(Include))
```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

# write.csv(voyages_url, here::here("data","proactive", paste('GHA_Q2_test','-', Sys.Date(),".csv", sep='')), row.names=F)

```

## add port info
```{r add in port information for CIV using anchorage stops}
anchorages <- fishwatchr::gfw_query(query = c("SELECT s2id, lat, lon, label, sublabel FROM `world-fishing-827.anchorages.named_anchorages_v20240117` WHERE iso3 = 'CIV'"),
                       run_query = TRUE,
                       con = con)$data

# write.csv(anchorages, here::here("data","proactive","2025_q1", paste('Abidjan_anchorages','_', Sys.Date(),".csv", sep='')), row.names=F)

table(anchorages$sublabel)

# s2ids for port features of interest 
vridi <- filter(anchorages, sublabel == 'ABIDJAN VRIDI')$s2id
lagoon <- filter(anchorages, sublabel == 'ABIDJAN LAGOON')$s2id
cargo <- filter(anchorages, sublabel == 'ABIDJAN TREICHVILLE CARGO')$s2id
fish <- filter(anchorages, sublabel == 'ABIDJAN TREICHVILLE FISHING')$s2id
offshore <- filter(anchorages, sublabel %in% c('ABIDJAN OFFSHORE', 'PORT BOUET', 'ABIDJAN PORT BOUET OFFSHORE'))$s2id

# getting bugs so changing order
port_stops <- voyages_url %>%
  rowwise() %>%
  mutate(abj_fishing = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% fish),
         abj_lagoon = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% lagoon),
         abj_vridi = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% vridi),
         abj_cargo = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% cargo),
         abj_offshore = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% offshore))

# table test of outputs 
table(port_stops$abj_fishing)
table(port_stops$abj_vridi)
table(port_stops$abj_offshore)
table(port_stops$abj_cargo)
table(port_stops$abj_lagoon)
```

## formatting
```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(port_stops, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= ais_mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, at_dock=dock, abj_lagoon, abj_vridi, abj_cargo, abj_fishing, abj_offshore, fishing=fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter= encounter, num_encounters=num_encounters, loitering=loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url)
   #gaps=1, num_gaps, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- voyages_reformat$fishing_hs >0

# write out data for initial TMT QA - SKIP for second round corrections
# write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)

```

## round 2 corrections
```{r make adjustments from TMT feedback, echo=F, warning=F, include=FALSE}

# remove any domestic vessels (use stripped string of country variable)
voyages_reformat <- voyages_reformat %>% filter(Flag != gsub("'", "", !!country_iso3))

# name corrections
voyages_reformat$vessel_name[voyages_reformat$MMSI %in% c(412329513)] <- 'LU RONG YUAN YU 215'

# remove duplicate/overlapping voyage from manual correction to LU QING YUAN YU 028
voyages_reformat <- voyages_reformat %>% filter(!(MMSI == 412331033 & trip_start == ymd_hms("2024-10-20 08:59:34")))

write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)

# CIV_Q4_2025 <- read.csv(here::here("data", "proactive", "q4_2025", "CIV_Q4_2025____.csv"), header=T) 

```

## pull fishing data
```{r CIV pull in the fishing data, echo=F, warning=F, include=FALSE}

q_fishing_events <- readr::read_file(here::here("queries","proactive", "proactive_fishing_locations.sql"))

fishing_civ <- fishwatchr::gfw_query(query = glue::glue(q_fishing_events,
                                               voyages_table = "`world-fishing-827.scratch_joef.civ_q4_25_all_voyages_temp`" 
                                               ),
                                 run_query = TRUE,
                                 con = con)$data

# sense check the data 
fishing_civ %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

table(voyages_reformat$vessel_class)

# add gear from TMT review - filter to only fishing vessels included in proactive analysis
gear_civ <- distinct(dplyr::select(voyages_reformat, MMSI, Flag, vessel_class, vessel_type)) %>% 
            mutate(ssvid=as.character(MMSI)) %>% 
            filter(grepl("fishing", vessel_class, ignore.case = TRUE))

# inner join to only include fishing events by fishing vessels
fishing_data_civ <- inner_join(fishing_civ, gear_civ, by = join_by(ssvid))

# remove fishing events outside of correct voyages (result of manual voyage add)
fishing_data_civ <- fishing_data_civ %>%
  semi_join(
    voyages_reformat, 
    by = join_by(
      MMSI,                             # Exact match on ID
      between(event_start, trip_start, trip_end) # Range match on time
    )
  )

table(fishing_data_civ$vessel_type)


```

## plot purse seine
```{r CIV voyage activity longline maps, echo=F, warning=F, include=FALSE}
# bin the data
fishing_data_civ$lat_bin <- round(fishing_data_civ$lat_mean/0.5)*0.5
fishing_data_civ$lon_bin <- round(fishing_data_civ$lon_mean/0.5)*0.5

# count positions in each lat lon bin
ps_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data_civ, grepl("seine", vessel_type, ignore.case = TRUE)) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )


# look at data distribution
quantile(ps_raster$fishing_hours)

# set upper limit
up_lim <- 350
#set plot center 
new_center <- 40

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-30, 10),
                          ylim = c(10, -10),
                          output_crs = best_proj)

# map for ps fishing 
ps_full <- ps_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(ps_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q4_25_proactive', paste0(country,"_", month,"_", "ps_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 15, 
       height = 17,
       bg = '#f7f7f7')

```
## trawl figs
```{r SEN voyage activity trawl maps, echo=F, warning=F, include=FALSE}
# add a different lat lon bin 
fishing_data_civ$lat_bin <- round(fishing_data_civ$lat_mean/0.5)*0.5
fishing_data_civ$lon_bin <- round(fishing_data_civ$lon_mean/0.5)*0.5

# count positions in each lat lon bin
trawl_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data_civ, grepl("trawl", vessel_type, ignore.case = TRUE)) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 300 
#set plot center 
new_center <- 17

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=17 +wktext"


# set plot limits bound on the data
bounding_wa <- transform_box(xlim = c(-8, 0),
                          ylim = c(6, 0),
                          output_crs = best_proj)

# trawl map 
trawl_full <- trawl_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                       limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_wa$box_out[['xmin']], bounding_wa$box_out[['xmax']]),
      ylim = c(bounding_wa$box_out[['ymin']], bounding_wa$box_out[['ymax']]),
      crs = bounding_wa$out_crs) +
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light')  +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(trawl_full,
                             main_box = bounding_wa,
                             globe_rel_size = '0.3',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures', 'q4_25_proactive', paste0(country,"_", month,"_", "trawl_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 12, 
       height = 16,
       bg = '#f7f7f7')

```
## plot carriers
```{r import voyage ais data for Abidjan q2voyages, echo=F, include=F, warning=F}

start_date <- "'2025-10-01 00:00:00 UTC'"
end_date <- "'2026-02-01 00:00:00 UTC'"
voyages_table <- "`world-fishing-827.scratch_joef.civ_q4_25_all_voyages_temp`"

# get list of carriers from TMT review - use grepl as vessel class text can vary
carrier_ssvids <-
voyages_reformat %>% 
  filter(grepl("carrier", vessel_class, ignore.case = TRUE)) %>% 
  pull(MMSI) 

# reformat to put into BQ
carrier_ssvids <-paste(paste0("'", carrier_ssvids, "'"), collapse = ", ")

voyages_ais_q <- readr::read_file(here::here("queries","proactive", "quarterly_carrier_ais.sql"))

voyage_ais_civ <- fishwatchr::gfw_query(query = glue::glue(voyages_ais_q, 
                                    start_date = start_date,
                                    end_date = end_date,
                                    voyage_table = voyages_table, 
                                    carrier_ssvids = carrier_ssvids),
                                 run_query = TRUE,
                                 con = con)$data
```

```{r Make a voyage line plot map, echo=F, warning=F}

#set plot center 
# new_center <- -15
new_center <- 2.5

# set proj for bounding box
# best_proj <- "+proj=eqearth +lon_0=-15 +wktext"
best_proj <- "+proj=eqearth +lon_0=2.5 +wktext"

# set plot limits for Atlantic 
# bounding_atlan <- transform_box(xlim = c(-70, 20),
#                           ylim = c(-55, 55),
#                           output_crs = best_proj)

bounding_atlan <- transform_box(xlim = c(-65, 20),
                          ylim = c(-55, 50),
                          output_crs = best_proj)

# rename voyage ais legend
# voyage_ais_civ$colour[voyage_ais$colour == 'port_profile'] <- 
voyage_ais_civ$colour[voyage_ais_civ$colour == 'quarter'] <- 'q4_voyage'
  
# make track into sf object 
voyage_ais_line <- voyage_ais_civ %>%
  dplyr::select(trip_id,colour, timestamp, lat, lon) %>%
  sf::st_as_sf(., 
               coords = c("lon", "lat"), 
               crs = 4326) %>%
  group_by(trip_id, colour) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)

# make make   
q_carrier_map <- 
  ggplot() +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  geom_sf(data = voyage_ais_line, aes(colour=colour), alpha=0.2, linewidth = 1.5) +
  scale_colour_manual(values=rev(gfw_palettes[['primary']])) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bounding_atlan$box_out[['xmin']], bounding_atlan$box_out[['xmax']]),
           ylim = c(bounding_atlan$box_out[['ymin']], bounding_atlan$box_out[['ymax']]),
           crs = bounding_atlan$out_crs) 

# add globe# add globevalues()
q_carrier_map_glob <- fishwatchr::add_little_globe(q_carrier_map,
                             main_box = bounding_atlan,
                             globe_rel_size = 0.3,
                             globe_just = 'inside',
                             globe_position = 'upperleft')  
  
# save object 
ggsave(q_carrier_map_glob, 
       filename = here::here('outputs','figures','q4_25_proactive',
                             paste('CIV_q4_carrier_lines_highres_v',Sys.Date(),'.png', sep='')), 
       width = 8, 
       height = 10)

```


# Ghana 

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}

country_iso3 <- "'GHA'"
# port_name <- "'ABIDJAN'"

# file names
month <- 'Q4'
country <- 'GHA'
           
# potential MMSIs to force in (should all be in master..)
missing_ssvids <- '""'

missing_ssvids <- c(missing_ssvids_manual, ssvid_master_include) %>% paste0("'", ., "'", collapse = ", ")
```

## add manual voyages if needed
```{r}

### add manual voyage and vessel details

# MAAN FARN NO.1- good prev visit in SEN, c1 arrival in GHA
row1 <- data.frame(
  year = 2025,
  ssvid = "416004904",
  vessel_id = "dc4940890-0883-9dd7-797b-ce8edfc33b2d",
  vessel_iso3 = "TWN",
  class_confidence = "2",
  vessel_class = "Fishing vessel",
  gear_type = "drifting_longlines",
  trip_id = "manual_add",
  trip_start = as.POSIXct("2025-10-12 15:06:08", tz = "UTC"),
  trip_end = as.POSIXct("2025-11-24 06:35:43", tz = "UTC"),
  trip_start_anchorage_id = "0ec176c1",
  trip_end_anchorage_id = "10207713",
  trip_start_visit_id = "be2be02c21c2d2f41c5165f50d52418a",
  trip_end_visit_id = "56222cbb0e9749a9c03eeca51d3e4955",
  trip_start_confidence = 4,
  trip_end_confidence = 1,
  start_label = "DAKAR",
  start_iso3 = "SEN",
  end_label = "TEMA",
  end_iso3 = "GHA",
    stringsAsFactors = FALSE
)

missing_voyages_df <- bind_rows(row1)

# Convert to SQL string
manual_voyage_cte <- manual_voyage_fxn(missing_voyages_df, cte_name = "manual_voyage_data")

```
## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.gha_q4_25_all_voyages_temp`'

# load query
voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_q4_2025.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    missing_ssvids = missing_ssvids,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3,
                                                    prev_visit_search_date = prev_visit_search_date),
                                                    manual_voyage_cte = manual_voyage_cte, # manual voyage 
                                 run_query = TRUE,
                                 con = con)

```
## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage_gha <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```
## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}

# use QA master vessel list from TMT for identity corrections 
# tmt_masterlist

# reset ssvid to character
# tmt_masterlist$ssvid <- as.character(tmt_masterlist$ssvid)

# Join update data to main data - CHECK to make sure no duplicates
merged_df <- left_join(voyages_with_coverage_gha, tmt_masterlist, by = "ssvid", suffix = c("", "_tmt"))

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}
# filter out the values from the master spreadsheet we shouldn't include
merged_df <- filter(merged_df, Include == 'Yes' | is.na(Include))

```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```

## add port info
```{r add in port information for Ghana using anchorage stops}
# s2ids for port features of interest 
tema_general <- c("102078b1", "102078bb", "102078a5", "102078a3", "102078bd", "10207899")
tema_fuel <- c("102078bf")
tema_fishing <- c("102078b7", "102078c7", "102078b9")
tema_offshore <- c("0fdf8781","0fdf8785","0fdf8787","0fdf8789","0fdf878b","0fdf878d","0fdf878f","0fdf87ed","0fdf87f1","0fdf87f3","0fdf87f5","0fdf87f7","0fdf87f9","0fdf87fd","0fdf87ff","0fdf8801","0fdf8803","102070ab","1020770b","10207713","10207715","10207743","10207745","10207747","10207749","1020774f","10207753","10207755","10207757","10207759","1020775b","1020775d","1020775f","10207761","10207763","10207765","10207767","10207769","1020776b","1020776d","1020776f","10207771","10207773","10207775","10207777","10207779","1020777b","1020777d","1020777f","10207781","10207783","10207785","10207787","10207789","1020778b","1020778d","1020778f","10207791","10207793","10207795","10207797","10207799","1020779b","1020779d","1020779f","102077a1","102077a3","102077a5","102077bd","102077c3","102077e1","102077e3","102077e5","102077e7","102077e9","102077eb","102077ed","102077ef","102077f1","102077f3","102077f5","102077f7","102077f9","102077fb","102077fd","102077ff","10207801","10207803","10207805","10207807","10207809","1020780b","1020780d","1020780f","10207811","10207813","10207815","10207817","10207819","1020781b","1020781d","1020781f","10207821","10207823","10207825","10207827","10207829","1020782b","1020782d","1020782f","10207831","10207833","10207835","10207837","10207839","1020783b","1020783d","1020783f","10207841","10207843","10207845","10207847","10207849","1020784b","1020784d","1020784f","10207851","10207853","10207855","10207857","10207859","1020785b","1020785d","1020785f","10207861","10207863","10207865","10207867","10207869","1020786b","1020786d","1020786f","10207871","10207873","10207875","10207877","10207879","1020787b","1020787d","1020787f","10207881","10207885","10207887","10207889","1020788b","1020788d","1020788f","10207891","10207893","10207895","102078e1","102078e3","102078e5","102078e7","102078e9","102078eb","102078ed","102078ef","102078f1","102078f3","102078f5","102078f7","102078f9","102078fb","102078fd","102078ff","10207901","10207903","10207905","10207907","10207909","1020791b","1020791d","10207991","10207993","10207995","10207997","10207999","102079a3","102079a5","102079a7","102079a9","102079ab","102079ad","102079af","102079b1","102079b3","102079b5","102079b7","102079b9","102079bb","102079bd","102079bf","102079c1","102079c3","102079c5","102079c7","102079c9","102079cb","102079cd","102079cf","102079d1","102079d3","102079d5","102079d7","102079d9","102079db","102079dd","102079df","102079e1","102079e3","102079e5","102079e7","102079e9","102079eb","102079ed","102079ef","102079f1","102079f3","102079f9","102079fb","102079fd","102079ff","10207be3","10207eab")
takoradi_general <- c("0fe770a9", "0fe770a7", "0fe770a1", "0fe770a3", "0fe770a5", "0fe770af")
takoradi_north <- c("0fe77a09", "0fe77a0b")
sekondi_takoradi <- c("0fe77b3d", "0fe77b17", "0fe77b11", "0fe77b05", "0fe77b1b", "0fe77b19", "0fe77b1d")
takoradi_offshore <- c("0fe7654b","0fe76fdd","0fe76fdf","0fe76fe1","0fe76ff9","0fe76fff","0fe77003","0fe77005","0fe77007","0fe77009","0fe7700b","0fe7700d","0fe7700f","0fe77011","0fe77013","0fe77015","0fe77017","0fe77019","0fe7701b","0fe7701d","0fe7701f","0fe77021","0fe77023","0fe7703d","0fe7703f","0fe77041","0fe77043","0fe77069","0fe7706b","0fe7706d","0fe7706f","0fe77071","0fe77073","0fe77075","0fe77077","0fe7707b","0fe77a5d","0fe77a5f","0fe77a61","0fe77a63","0fe77a65","0fe77a67","0fe77a83","0fe77a85","0fe77a87","0fe77a89","0fe77a8b","0fe77a8d","0fe77a8f","0fe77a91","0fe77a93","0fe77a95","0fe77a97","0fe77a99","0fe77a9b","0fe77a9d","0fe77a9f","0fe77aa1","0fe77aa3","0fe77aa5","0fe77aa7","0fe77aa9","0fe77aab","0fe77aad","0fe77aaf","0fe77ab1","0fe77ab3","0fe77ab5","0fe77ab7","0fe77ab9","0fe77abb","0fe77abd","0fe77abf","0fe77ac1","0fe77ac3","0fe77ac5","0fe77ac7","0fe77ac9","0fe77aeb","0fe77aed","0fe77af3","0fe77af5")

# add logic column to indicate presence at each location of interest 
voyages_url$tema_general <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% tema_general)
})

voyages_url$tema_fuel <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% tema_fuel)
})

voyages_url$tema_fishing <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% tema_fishing)
})

voyages_url$tema_offshore <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% tema_offshore)
})

voyages_url$takoradi_general <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% takoradi_general)
})

voyages_url$takoradi_north <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% takoradi_north)
})

voyages_url$sekondi_takoradi <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% sekondi_takoradi)
})

voyages_url$takoradi_offshore <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% takoradi_offshore)
})

```

## formatting
```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(voyages_url, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= ais_mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, at_dock=dock, tema_general, tema_fuel, tema_fishing, tema_offshore, takoradi_general, takoradi_north, sekondi_takoradi, takoradi_offshore, num_fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter, num_encounters, loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url) #, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- ifelse(is.na(voyages_reformat$fishing_hs), FALSE, TRUE)

# write out data for initial TMT QA - SKIP for second round corrections
# write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

## round 2 corrections
```{r make adjustments from TMT feedback in GHA, echo=F, warning=F, include=FALSE}

# remove any domestic vessels (use stripped string of country variable)
voyages_reformat <- voyages_reformat %>% filter(Flag != gsub("'", "", !!country_iso3))

write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)

```

## pull gha fishing data
```{r import voyage ais data for Ghana q2voyages, echo=F, include=F, warning=F}

q_fishing_events <- readr::read_file(here::here("queries","proactive", "proactive_fishing_locations.sql"))

fishing_gha <- fishwatchr::gfw_query(query = glue::glue(q_fishing_events,
                                               voyages_table = "`world-fishing-827.scratch_joef.gha_q4_25_all_voyages_temp`" 
                                               ),
                                 run_query = TRUE,
                                 con = con)$data

# deduplicate (possible with manual voyages)
fishing_gha <- fishing_gha %>% distinct()

# sense check the data 
fishing_gha %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

# add gear from TMT review - filter to only fishing vessels included in proactive analysis
gear_gha <- distinct(dplyr::select(voyages_reformat, MMSI, Flag, vessel_class, vessel_type)) %>% 
            mutate(ssvid=as.character(MMSI)) %>% 
            filter(grepl("fishing", vessel_class, ignore.case = TRUE))

# inner join to only include fishing events by fishing vessels
fishing_data_gha <- inner_join(fishing_gha, gear_gha, by = join_by(ssvid))

table(fishing_data_gha$vessel_type)
```

## LL figs
```{r GHA voyage activity longline maps, echo=F, warning=F, include=FALSE}

# bin the data
fishing_data_gha$lat_bin <- round(fishing_data_gha$lat_mean/0.5)*0.5
fishing_data_gha$lon_bin <- round(fishing_data_gha$lon_mean/0.5)*0.5

table(fishing_data_gha$vessel_type)

# select the longline events only
ll <- fishing_data_gha %>% filter(grepl("longline", vessel_type, ignore.case = TRUE))

# count positions in each lat lon bin
longline_raster <- 
  ll %>% 
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# 
quantile(longline_raster$fishing_hours)

# set upper limit
up_lim <- 200 
#set plot center 
new_center <- 40

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-50, 5),
                          ylim = c(30, -5),
                          output_crs = best_proj)

# map for atlantic longline 
atl_full <- longline_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(atl_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q4_25_proactive', paste0(country,"_", month,"_", "longline_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 17, 
       height = 16,
       bg = '#f7f7f7')

```

## purse seine fig
```{r SEN voyage activity trawl maps, echo=F, warning=F, include=FALSE}
# bin the data
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.1)*0.1
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.1)*0.1

# count positions in each lat lon bin
ps_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data_gha, grepl("seine", vessel_type, ignore.case = TRUE)) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 100 
#set plot center 
new_center <- 17

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=17 +wktext"


# set plot limits bound on the data
bounding_wa <- transform_box(xlim = c(-5, 5),
                          ylim = c(10, -2),
                          output_crs = best_proj)

# ps map 
ps_full <- ps_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                       limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_wa$box_out[['xmin']], bounding_wa$box_out[['xmax']]),
      ylim = c(bounding_wa$box_out[['ymin']], bounding_wa$box_out[['ymax']]),
      crs = bounding_wa$out_crs) +
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light')  +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(ps_full,
                             main_box = bounding_wa,
                             globe_rel_size = '0.3',
                             globe_just = 'inside',
                             globe_position = 'upperleft')

ggsave(filename = here::here('outputs', 'figures', 'q4_25_proactive', paste0(country,"_", month,"_", "ps_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 12, 
       height = 16,
       bg = '#f7f7f7')

```

## plot gha carriers
```{r import voyage ais data for Ghana q4voyages, echo=F, include=F, warning=F}
start_date <- "'2025-10-01 00:00:00 UTC'"
end_date <- "'2026-02-01 00:00:00 UTC'"
voyages_table <- "`world-fishing-827.scratch_joef.gha_q4_25_all_voyages_temp`"

# get list of carriers from TMT review - use grepl as vessel class text can vary
carrier_ssvids <-
voyages_reformat %>% 
  select(vessel_class, MMSI) %>% distinct() %>% 
  filter(grepl("carrier", vessel_class, ignore.case = TRUE)) %>% 
  pull(MMSI) 

# reformat to put into BQ
carrier_ssvids <-paste(paste0("'", carrier_ssvids, "'"), collapse = ", ")

voyages_ais_q <- readr::read_file(here::here("queries","proactive", "quarterly_carrier_ais.sql"))

voyage_ais_gha <- fishwatchr::gfw_query(query = glue::glue(voyages_ais_q, 
                                    start_date = start_date,
                                    end_date = end_date,
                                    voyage_table = voyages_table, 
                                    carrier_ssvids = carrier_ssvids),
                                 run_query = TRUE,
                                 con = con)$data

voyage_ais_gha %>% distinct() %>% View()

```

```{r Make a gha voyage line plot map, echo=F, warning=F}
#set plot center 
new_center <- -15

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=-15 +wktext"

# set plot limits for Atlantic 
bounding_atlan <- transform_box(xlim = c(-30, 20),
                          ylim = c(-10, 35),
                          output_crs = best_proj)
bounding_atlan <- transform_box(xlim = c(-80, 20),
                          ylim = c(-55, 50),
                          output_crs = best_proj)
# rename voyage ais legend
# voyage_ais$colour[voyage_ais$colour == 'port_profile'] <- 'q2_voyage'
voyage_ais_gha$colour[voyage_ais_gha$colour == 'quarter'] <- 'q3_voyage'

#voyage_ais$colour[voyage_ais$colour == ''] <-
  
# make track into sf object 
voyage_ais_line <- voyage_ais_gha %>%
  dplyr::select(trip_id,colour, timestamp, lat, lon) %>%
  sf::st_as_sf(., 
               coords = c("lon", "lat"), 
               crs = 4326) %>%
  group_by(trip_id, colour) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)

# make make   
q_carrier_map <- 
  ggplot() +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  geom_sf(data = voyage_ais_line, aes(colour=colour), alpha=0.2, linewidth = 1.5) +
  scale_colour_manual(values=rev(gfw_palettes[['primary']])) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bounding_atlan$box_out[['xmin']], bounding_atlan$box_out[['xmax']]),
           ylim = c(bounding_atlan$box_out[['ymin']], bounding_atlan$box_out[['ymax']]),
           crs = bounding_atlan$out_crs) 

# add globe# add globevalues()
q_carrier_map_glob <- fishwatchr::add_little_globe(q_carrier_map,
                             main_box = bounding_atlan,
                             globe_rel_size = 0.25,
                             globe_just = 'inside',
                             globe_position = 'upperright')  
  
# save object 
ggsave(q_carrier_map_glob, 
       filename = here::here('outputs','figures','q4_25_proactive',
                             paste('GHA_q4_carrier_lines_highres_v',Sys.Date(),'.png', sep='')), 
       width = 8, 
       height = 10)

```


# Senegal  

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}

country_iso3 <- "'SEN'"
# port_name <- "'DAKAR'"

# file names
month <- 'Q4'
country <- 'SEN'

# potential MMSIs to force in 
missing_ssvids <- ''

missing_ssvids <- c(missing_ssvids, ssvid_master_include) %>% paste0("'", ., "'", collapse = ", ")

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.sen_q4_25_all_voyages_temp`'

```

## add manual voyages if needed
```{r}
# Your manually entered missing data
# Cure
row1 <- data.frame(
  year = 2025,
  ssvid = "629009188",
  vessel_id = "ae51bd83f-f41a-8f60-712e-499e3e4ef2c1",
  vessel_iso3 = "GMB",
  class_confidence = "1",
  vessel_class = "Fishing vessel",
  gear_type = "",
  trip_id = "manual_add_1",
  trip_start = as.POSIXct("2025-12-12 22:55:05", tz = "UTC"),
  trip_end = as.POSIXct("2025-12-29 18:30:22", tz = "UTC"),
  trip_start_anchorage_id = "0ea1b22b",
  trip_end_anchorage_id = "0ec17255",
  trip_start_visit_id = "85bfdf501f5b7ee54f74a9767ccd7997",
  trip_end_visit_id = "6f590e2d2c359a2868ef7781608e7c61",
  trip_start_confidence = 2,
  trip_end_confidence = 3,
  start_label = "NOUADHIBOU",
  start_iso3 = "MRT",
  end_label = "DAKAR",
  end_iso3 = "SEN",
    stringsAsFactors = FALSE
)

# LUQINGYUANYU199 
row2 <- data.frame(
  year = 2025,
  ssvid = "412371178",
  vessel_id = "4816d2eaa-a8ef-d96e-585b-5262e7324dac",
  vessel_iso3 = "CHN",
  class_confidence = "1",
  vessel_class = "Fishing vessel",
  gear_type = "drifting_longlines",
  trip_id = "manual_add_2",
  trip_start = as.POSIXct("2025-09-04 15:58:18", tz = "UTC"),
  trip_end = as.POSIXct("2026-01-31 13:59:59", tz = "UTC"),
  trip_start_anchorage_id = "0ec1741b",
  trip_end_anchorage_id = "0ea1b22b",
  trip_start_visit_id = "7d4d51bdc8d0021c6d64c49cece608f8",
  trip_end_visit_id = "7efd20a943ff6e51fae18ad6b29b49d8",
  trip_start_confidence = 4,
  trip_end_confidence = 3,
  start_label = "DAKAR",
  start_iso3 = "SEN",
  end_label = "DAKAR",
  end_iso3 = "SEN",
    stringsAsFactors = FALSE
)

# FU YUAN YU 7857 - long voyage bc of duplicate vessel_ids - need to delete extra
row3 <- data.frame(
  year = 2025,
  ssvid = "412440842",
  vessel_id = "37d18a147-79f8-1fdc-3e0d-2baa5b6f4631",
  vessel_iso3 = "CHN",
  class_confidence = "1",
  vessel_class = "Fishing vessel",
  gear_type = "drifting_longlines",
  trip_id = "manual_add_3",
  trip_start = as.POSIXct("2025-10-28 02:43:53", tz = "UTC"),
  trip_end = as.POSIXct("2025-12-28 07:49:15", tz = "UTC"),
  trip_start_anchorage_id = "0ec173af",
  trip_end_anchorage_id = "0ec1741b",
  trip_start_visit_id = "a8f1f85cc14d9d356fb2e23ae41e262a",
  trip_end_visit_id = "4a94277860e0297049f858b7eb997d63",
  trip_start_confidence = 4,
  trip_end_confidence = 4,
  start_label = "DAKAR",
  start_iso3 = "SEN",
  end_label = "DAKAR",
  end_iso3 = "SEN",
    stringsAsFactors = FALSE
)

# SHENGHANG808 - not a clear departure before the one recorded to make voyage, although 2 dakar visits in Q4 (diff vessel_ids)
# row4 <- data.frame(
#   year = 2025,
#   ssvid = "412209211",
#   vessel_id = "37d18a147-79f8-1fdc-3e0d-2baa5b6f4631",
#   vessel_iso3 = "CHN",
#   class_confidence = "1",
#   vessel_class = "Fishing vessel",
#   gear_type = "drifting_longlines",
#   trip_id = "manual_add_4",
#   trip_start = as.POSIXct("2025-10-28 02:43:53", tz = "UTC"),
#   trip_end = as.POSIXct("2025-12-28 07:49:15", tz = "UTC"),
#   trip_start_anchorage_id = "0ec173af",
#   trip_end_anchorage_id = "0ec1741b",
#   trip_start_visit_id = "a8f1f85cc14d9d356fb2e23ae41e262a",
#   trip_end_visit_id = "4a94277860e0297049f858b7eb997d63",
#   trip_start_confidence = 4,
#   trip_end_confidence = 4,
#   start_label = "DAKAR",
#   start_iso3 = "SEN",
#   end_label = "DAKAR",
#   end_iso3 = "SEN",
#     stringsAsFactors = FALSE
# )

missing_voyages_df <- bind_rows(row1, row2, row3)

# Convert to SQL string
manual_voyage_cte <- manual_voyage_fxn(missing_voyages_df, cte_name = "manual_voyage_data")

```

## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_q4_2025.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    missing_ssvids = missing_ssvids,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3,
                                                    prev_visit_search_date = prev_visit_search_date),
                                                    manual_voyage_cte = manual_voyage_cte, # manual voyage 
                                 run_query = TRUE,
                                 con = con)

```

## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```

## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}
# use master QA list from TMT for identity corrections 

# reset ssvid to character
tmt_masterlist$ssvid <- as.character(tmt_masterlist$ssvid)

# Join update data to main data - CHECK to make sure no duplicates
merged_df <- left_join(voyages_with_coverage, tmt_masterlist, by = "ssvid", suffix = c("", "_tmt"))

#filter(merged_df, ssvid=='412209123')

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}
 

merged_df <- filter(merged_df, Include != 'No' | is.na(Include))

```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```

## add port info
```{r add in port information for SEN using anchorage stops}
anchorages <- fishwatchr::gfw_query(query = c("SELECT s2id, lat, lon, label, sublabel FROM `world-fishing-827.anchorages.named_anchorages_v20240117` WHERE iso3 = 'SEN'"),
                       run_query = TRUE,
                       con = con)$data

table(anchorages$sublabel)

# s2ids for port features of interest 
container <- c("0ec173a9")
east_basin <- c("0ec173b1")
mid_basin <- c("0ec173b3")
west_basin <- c("0ec173ad")
entrance <- c("0ec173af")
navy <- c("0ec17253")
dak_fishing <- c("0ec17301", "0ec173ab", "0ec172ff", "0ec17255")

# large number of anchorages outside dakar - define with lat/lon box
dak_anchorage <- filter(anchorages, 
                        between(lat, 14.61, 14.72), 
                        between(lon, -17.42, -17.3))

dak_offshore <- dak_anchorage$s2id 


port_stops <- voyages_url %>%
  rowwise() %>%
  mutate(entrance = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% entrance),
         container = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% container),
         navy = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% navy),
         mid_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% mid_basin),
         east_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% east_basin),
         west_basin = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% west_basin),
         dak_fishing = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% dak_fishing),
         dak_offshore = any(str_trim(str_split(stop_anchorage_ids, ",")[[1]]) %in% dak_offshore))

table(port_stops$dak_fishing)
```


```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(port_stops, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= ais_mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label,prev_visit_timestamp, entrance, navy, west_basin, mid_basin, east_basin, container, dak_fishing, dak_offshore, fishing = num_fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter, num_encounters, loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url) #, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- ifelse(is.na(voyages_reformat$fishing_hs), FALSE, TRUE)

# write out data for initial TMT QA - SKIP for follow up round
# write.csv(arrange(voyages_reformat, trip_end), here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),".csv", sep='')), row.names=F)
```

## round 2 corrections
```{r make adjustments from TMT feedback in SEN, echo=F, warning=F, include=FALSE}

# remove any domestic vessels (use stripped string of country variable)
voyages_reformat <- voyages_reformat %>% filter(Flag != gsub("'", "", !!country_iso3))

# name corrections
voyages_reformat$vessel_name[voyages_reformat$MMSI %in% c(412200985)] <- 'LUQINGYUANYU 056'

# write out v2 dataset
write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)
```

## LL figs
```{r SEN pull in the fishing data, echo=F, warning=F, include=FALSE}

q_confidence <- readr::read_file(here::here("queries", "proactive", "proactive_fishing_locations.sql"))

fishing <- fishwatchr::gfw_query(query = glue::glue(q_confidence,
                                               voyages_table = temp_table_voyages
                                               ),
                                 run_query = TRUE,
                                 con = con)$data

# deduplicate (possible with manual voyages)
fishing <- fishing %>% distinct()

# sense check the data 
fishing %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

# add gear from TMT review - filter to only fishing vessels included in proactive analysis
gear <- distinct(dplyr::select(voyages_reformat, MMSI, Flag, vessel_class_cat, vessel_class, vessel_type)) %>% 
            mutate(ssvid=as.character(MMSI)) %>% 
            filter(grepl("fishing", vessel_class, ignore.case = TRUE))

# inner join to only include fishing events by fishing vessels
fishing_data <- inner_join(fishing, gear, by = join_by(ssvid))

table(fishing_data$vessel_type, fishing_data$vessel_name)
```

```{r SEN voyage activity longline maps, echo=F, warning=F, include=FALSE}

# bin the data
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.5)*0.5
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.5)*0.5

table(fishing_data$vessel_type)

# select the longline events only
# ll <- filter(fishing_data, vessel_type %in% c('drifting_longlines', 'drifting_longline', 'Longline', 'set_longlines'))
ll <- fishing_data %>% filter(grepl("longline", vessel_type, ignore.case = TRUE))

# look at activity which isn't in main distribution of longline vessels 
likely_non_ll <- filter(ll,
                        between(lat_mean, 11, 14),
                        between(lon_mean, -18, -16))

# count positions in each lat lon bin
longline_raster <- 
  # filter out low speeds while vessel in port (? - not doing this it seems..)
  # filter(ll, vessel_type %in%  c('drifting_longlines', 'drifting_longline', 'Longline', 'set_longlines')) %>% don't need this as filtered above
  ll %>% 
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 500 
#set plot center 
new_center <- 40

# 
quantile(longline_raster$fishing_hours)

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-40, 20),
                          ylim = c(15, -30),
                          output_crs = best_proj)

# map for atlantic longline 
atl_full <- longline_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(atl_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q4_25_proactive', paste0(country,"_", month,"_", "longline_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 17, 
       height = 16,
       bg = '#f7f7f7')

```

## trawl figs
```{r SEN voyage activity trawl maps, echo=F, warning=F, include=FALSE}
# add a different lat lon bin 
fishing_data$lat_bin <- round(fishing_data$lat_mean/0.1)*0.1
fishing_data$lon_bin <- round(fishing_data$lon_mean/0.1)*0.1


# count positions in each lat lon bin
trawl_raster <- 
  # filter out low speeds while vessel in port 
  filter(fishing_data, vessel_type %in% c('trawlers', 'Trawl')) %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# set upper limit
up_lim <- 9000 
#set plot center 
new_center <- 17

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=17 +wktext"


# set plot limits bound on the data
bounding_wa <- transform_box(xlim = c(-20, -14),
                          ylim = c(18, 8.5),
                          output_crs = best_proj)

# trawl map 
trawl_full <- trawl_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                       limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_wa$box_out[['xmin']], bounding_wa$box_out[['xmax']]),
      ylim = c(bounding_wa$box_out[['ymin']], bounding_wa$box_out[['ymax']]),
      crs = bounding_wa$out_crs) +
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light')  +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(trawl_full,
                             main_box = bounding_wa,
                             globe_rel_size = '0.5',
                             globe_just = 'inside',
                             globe_position = 'upperleft')

ggsave(filename = here::here('outputs', 'figures', 'q4_25_proactive', paste0(country,"_", month,"_", "trawl_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 12, 
       height = 16,
       bg = '#f7f7f7')

```



# Guinea  

## set parameters for analysis 

```{r set date and port parameters, echo=F, warning=F, include=FALSE}

country_iso3 <- "'GIN'"

# file names
month <- 'Q4'
country <- 'GIN'

# additional MMSIs to force in
missing_ssvids_manual <- c('')

missing_ssvids <- c(missing_ssvids_manual, ssvid_master_include) %>% paste0("'", ., "'", collapse = ", ")

```

## add manual voyages if needed
```{r}

### add manual voyage and vessel details - skip in voyage query if not relevant

missing_voyages_df <- ""

# Convert to SQL string
# manual_voyage_cte <- ""
#   manual_voyage_fxn(missing_voyages_df, cte_name = "manual_voyage_data")

```

## run voyage query
```{r voyages all, echo=F, warning=F, include=FALSE}

# create a temp table for query 
temp_table_voyages <- '`world-fishing-827.scratch_joef.gin_q4_25_all_voyages_temp`'

voyages_q <- readr::read_file(here::here("queries","proactive", "recent_country_activity_c2_q4_2025.sql"))

fishwatchr::gfw_query(query = glue::glue(voyages_q, 
                                                    start_date = start_date,
                                                    end_date = end_date,
                                                    start_year = start_year,
                                                    end_year = end_year,
                                                    missing_ssvids = missing_ssvids,
                                                    temp_table = temp_table_voyages,
                                                    port_iso = country_iso3,
                                                    prev_visit_search_date = prev_visit_search_date),
                                                    # manual_voyage_cte = manual_voyage_cte, # manual voyage 
                                 run_query = TRUE,
                                 con = con)

```


## run AIS query
```{r voyages ais coverage, echo=F, warning=F, include=FALSE}

ais_cov_q <- readr::read_file(here::here("queries","proactive", "voyage_ais_coverage_no_port.sql"))

voyages_with_coverage <- fishwatchr::gfw_query(query = glue::glue(ais_cov_q, 
                                                    temp_table = temp_table_voyages,
                                                    start_date = start_date,
                                                    end_date = end_date),
                                 run_query = TRUE,
                                 con = con)$data

```

## gear corrections
```{r gear type corrections from TMT data, echo=F, warning=F, include=FALSE}

# use master QA list from TMT for identity corrections 

# reset ssvid to character
tmt_masterlist$ssvid <- as.character(tmt_masterlist$ssvid)

# Join update data to main data - CHECK to make sure no duplicates
merged_df <- left_join(voyages_with_coverage, tmt_masterlist, by = "ssvid", suffix = c("", "_tmt"))

# update columns when they aren't NA 
# map columns to update
column_mapping <- list(
  vessel_flag_best = "CurrentFlag",
  vessel_class_best  = "VesselType",
  geartype_best = "GearType"            
)

# Replace values in gfw_df with tmt_df values (if not NA)
for (main_col in names(column_mapping)) {
  update_col <- column_mapping[[main_col]]
  if (update_col %in% names(merged_df)) {
    merged_df[[main_col]] <- ifelse(!is.na(merged_df[[update_col]]), 
                                     merged_df[[update_col]], 
                                     merged_df[[main_col]])
    # Optionally remove the update column after replacement
    merged_df[[update_col]] <- NULL
  }
}
 

merged_df <- filter(merged_df, Include != 'No' | is.na(Include))


```

## add urls
```{r add gfw hyperlink for voyage, echo=F, warning=F, include=FALSE}

# base componenets for VV string to accompany port profiles 
base_string_p1 <- 'https://globalfishingwatch.org/map/vessel/'
base_string_p2 <- '?&start='
base_string_p3 <- '&end='
start_date_url <- '2025-01-01'
end_date_url <- '2025-3-31'

#format(voyages_with_coverage$trip_start, format='%Y-%m-%d')

# paste string components together using vessel id, trip start and trip end from data 
voyages_url <- bind_cols(merged_df, 
                         vv_url = paste('=HYPERLINK("',
                          base_string_p1,
                          merged_df$vessel_id, 
                          base_string_p2, 
                          as.Date(format(merged_df$trip_start, format='%Y-%m-%d'))-2, 
                          base_string_p3, 
                          as.Date(format(merged_df$trip_end, format='%Y-%m-%d'))+2,
                          '")', sep=''))

```

## add port info
```{r add in port information for Ghana using anchorage stops}
# s2ids for port features of interest 
conakry_offshore <- c("0f1cc579", "0f1cc57d", "0f1cc57f", "0f1ccf81",
"0f1ccf87")
conakry_nearshore <- c("0f1cd011", "0f1cd015", "0f1cd063", "0f1cd065", "0f1cd067", "0f1cd071", "0f1cd073", "0f1cd07b", "0f1cd07d")
conakry_container_term <- c("0f1cd09b", "0f1cd09d")
conakry_oiljetty <- c("0f1cd0bb")
conakry_pq1 <- c("0f1cd099")
conakry_pq5 <- c("0f1cd0a3")
conakry_pq8 <- c("0f1cd0bd")


# add logic column to indicate presence at each location of interest 
voyages_url$conakry_offshore <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_offshore)
})

voyages_url$conakry_nearshore <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_nearshore)
})

voyages_url$conakry_container_term <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_container_term)
})

voyages_url$conakry_oiljetty <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_oiljetty)
})

voyages_url$conakry_pq1 <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_pq1)
})

voyages_url$conakry_pq5 <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_pq5)
})

voyages_url$conakry_pq8 <- sapply(voyages_url$stop_anchorage_ids, function(x) {
  any(strsplit(x, ",\\s*")[[1]] %in% conakry_pq8)
})


```
## formatting
```{r format the data to TMT format, echo=F, warning=F, include=FALSE}
# change colnames to be sensible for an externally shared document 
voyages_reformat <- dplyr::select(voyages_url, vessel_name=shipname, MMSI=ssvid,
   Flag=vessel_flag_best, AIS_Flag= ais_mmsi_flag, imo, vessel_class_cat=vessel_class_initial, vessel_class_confidence = class_confidence_initial, vessel_class=vessel_class_best,
   vessel_type=geartype_best,  previous_port_country = start_port_iso3,
   previous_port = start_port_label, trip_start, trip_start_confidence, trip_end, trip_end_confidence, trip_duration_days,
   end_port = end_port_label, prev_visit_timestamp, at_dock=dock, 
   conakry_offshore, conakry_nearshore, conakry_container_term, conakry_oiljetty, conakry_pq1, conakry_pq5, conakry_pq8,
   fishing=fishing, fishing_hours, fishing_eez=eezs, fishing_hs =high_seas, fishing_rfmos = rfmos, encounter= encounter, num_encounters=num_encounters, loitering=loitering, num_loitering, AISdisabling, num_AISdisabling, percent_ais_voyage=percent_ais_voyage, vv_url)
   #gaps=1, num_gaps, total_gap_hours)

# overwrite fishing_hs T/F
voyages_reformat$fishing_hs <- voyages_reformat$fishing_hs >0

# write out data for initial TMT QA - SKIP if round 2 edits
write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(), sep='')), row.names=F)

```

## round 2 corrections
```{r make adjustments from TMT feedback in GHA, echo=F, warning=F, include=FALSE}

# remove any domestic vessels (use stripped string of country variable)
voyages_reformat <- voyages_reformat %>% filter(Flag != gsub("'", "", !!country_iso3))

# name corrections
voyages_reformat$vessel_name[voyages_reformat$MMSI %in% c(228240000)] <- 'CHRIST DA 2'


write.csv(voyages_reformat, here::here("data", "proactive", "q4_2025", paste(country,'_', month,'_', year,'_', Sys.Date(),"_v2.csv", sep='')), row.names=F)

```

## plot gin fishing
```{r import voyage ais data for voyages, echo=F, include=F, warning=F}

q_fishing_events <- readr::read_file(here::here("queries","proactive", "proactive_fishing_locations.sql"))

fishing_gin <- fishwatchr::gfw_query(query = glue::glue(q_fishing_events,
                                               voyages_table = "`world-fishing-827.scratch_joef.gin_q4_25_all_voyages_temp`" 
                                               ),
                                 run_query = TRUE,
                                 con = con)$data


# sense check the data 
fishing_gin %>%
    group_by(ssvid) %>%
      summarise(positions = n(), 
                min_date = min(event_start), 
                max_date = max(event_end))

# add gear from TMT review - filter to only fishing vessels included in proactive analysis
gear_gin <- distinct(dplyr::select(voyages_reformat, MMSI, Flag, vessel_class_cat, vessel_class, vessel_type)) %>% 
            mutate(ssvid=as.character(MMSI)) %>% 
            filter(grepl("fishing", vessel_class, ignore.case = TRUE))

# inner join to only include fishing events by fishing vessels
fishing_data_gin <- inner_join(fishing_gin, gear_gin, by = join_by(ssvid))

table(fishing_data_gin$vessel_type)

# bin the data
fishing_data_gin$lat_bin <- round(fishing_data_gin$lat_mean/0.05)*0.05
fishing_data_gin$lon_bin <- round(fishing_data_gin$lon_mean/0.05)*0.05


# count positions in each lat lon bin
gin_fish_raster <- 
  # filter out low speeds while vessel in port 
  fishing_data_gin %>%
    group_by(lat_bin, lon_bin) %>%
      summarise(
        fishing_hours = sum(fishing_hours),
        vessels = n_distinct(ssvid)
      )

# look at data distribution
quantile(gin_fish_raster$fishing_hours)

# set upper limit
up_lim <- 300 
#set plot center 
new_center <- 40

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=40 +wktext"

# set plot limits bound on the data
bounding_atl <- transform_box(xlim = c(-20, -10),
                          ylim = c(13, 6),
                          output_crs = best_proj)

# map for atlantic purse seine 
atl_full <- gin_fish_raster %>%
  recenter_raster(raster_df = .,
                  res = 1,
                  x_lab = 'lon_bin',
                  y_lab = 'lat_bin',
                  fill_lab = 'fishing_hours',
                  center = new_center) %>% 
  ggplot()+
  geom_gfw_outline(center = new_center, theme = "dark") +
  geom_raster(aes(x= lon_bin, y=lat_bin, fill = fishing_hours)) +
    geom_gfw_eez(theme = 'dark', alpha = 0.9, center = new_center) +
    geom_gfw_land(theme = 'dark', center = new_center) +
    # geom_sf(pipa, fill=NA, colour='green')+
    scale_fill_gradientn(colors = gfw_palette('map_effort_dark'),
                      limits = c(0,up_lim),
                       oob = scales::squish,
                       na.value = NA) +   
    coord_sf(xlim = c(bounding_atl$box_out[['xmin']], bounding_atl$box_out[['xmax']]),
      ylim = c(bounding_atl$box_out[['ymin']], bounding_atl$box_out[['ymax']]),
      crs = bounding_atl$out_crs) +
    # scale_x_continuous(breaks = custom_breaks, labels = custom_labels)+
    labs(fill = 'Fishing Hours') +
    theme_gfw_map(theme = 'light') +
    theme(legend.text = element_text(family = 'Roboto',
                                 color = '#848b9b',
                                 size = 6),
        legend.title = element_text(family = 'Roboto',
                                  face = 'bold',
                                  color = '#363c4c',
                                  size = 6),
      legend.position = 'bottom',
      legend.box = 'vertical',
      legend.key.height = unit(2, 'mm'),
      legend.key.width = unit(15,'mm'))


fishwatchr::add_little_globe(atl_full,
                             main_box = bounding_atl,
                             globe_rel_size = '0.25',
                             globe_just = 'inside',
                             globe_position = 'upperright')

ggsave(filename = here::here('outputs', 'figures','q4_25_proactive', paste0(country,"_", month,"_", "ps_map-",str_replace_all(Sys.Date(), '-','_'),".png")), 
       units = 'cm', 
       width = 15, 
       height = 17,
       bg = '#f7f7f7')

```

## plot gin carriers
```{r import voyage ais data for gin voyages, echo=F, include=F, warning=F}

start_date <- "'2025-10-01 00:00:00 UTC'"
end_date <- "'2026-02-01 00:00:00 UTC'"
voyages_table <- "`world-fishing-827.scratch_joef.gin_q4_25_all_voyages_temp`"

table(voyages_reformat$vessel_type)

# get list of carriers from TMT review - use grepl as vessel class text can vary
carrier_ssvids <- ###unique(filter(voyages_reformat, vessel_class == 'carrier')$MMSI)
voyages_reformat %>% 
  filter(grepl("carrier", vessel_class, ignore.case = TRUE)) %>% 
  pull(MMSI)

# reformat to put into BQ
carrier_ssvids <-paste(paste0("'", carrier_ssvids, "'"), collapse = ", ")

voyages_ais_q <- readr::read_file(here::here("queries","proactive", "quarterly_carrier_ais.sql"))

voyage_ais_gin <- fishwatchr::gfw_query(query = glue::glue(voyages_ais_q, 
                                    start_date = start_date,
                                    end_date = end_date,
                                    voyage_table = voyages_table, 
                                    carrier_ssvids = carrier_ssvids),
                                 run_query = TRUE,
                                 con = con)$data

```

```{r Make a gin voyage line plot map, echo=F, warning=F}

#set plot center to centre of IO
new_center <- -15

# set proj for bounding box
best_proj <- "+proj=eqearth +lon_0=-15 +wktext"

# set plot limits for Atlantic 
# bounding_atlan <- transform_box(xlim = c(-70, 20),
#                           ylim = c(-55, 55),
#                           output_crs = best_proj)

bounding_atlan <- transform_box(xlim = c(-30, -10),
                          ylim = c(5, 20),
                          output_crs = best_proj)
# bounding_atlan <- transform_box(xlim = c(-65, 20),
#                           ylim = c(-55, 50),
#                           output_crs = best_proj)

# rename voyage ais legend
# voyage_ais$colour[voyage_ais$colour == 'port_profile'] <- 'q2_voyage'
voyage_ais_gin$colour[voyage_ais_gin$colour == 'quarter'] <- 'q3_voyage'

#voyage_ais$colour[voyage_ais$colour == ''] <-
  
# make track into sf object 
voyage_ais_line <- voyage_ais_gin %>%
  dplyr::select(trip_id,colour, timestamp, lat, lon) %>%
  sf::st_as_sf(., 
               coords = c("lon", "lat"), 
               crs = 4326) %>%
  group_by(trip_id, colour) %>%
  arrange(timestamp) %>%
  summarize(do_union = FALSE) %>%
  sf::st_cast(., "LINESTRING") %>%
  fishwatchr::recenter_sf(., center = new_center, buffer=0)

# make make   
q_carrier_map <- 
  ggplot() +
  geom_gfw_land(theme = 'dark', center = new_center) +
  geom_gfw_eez(theme = 'dark', alpha = 0.4, center = new_center) +
  geom_sf(data = voyage_ais_line, aes(colour=colour), alpha=0.2, linewidth = 1.5) +
  scale_colour_manual(values=rev(gfw_palettes[['primary']])) +
  theme_gfw_map(theme = "dark") +
  theme(legend.position="right") +
  labs(colour = 'MMSI') +
  coord_sf(xlim = c(bounding_atlan$box_out[['xmin']], bounding_atlan$box_out[['xmax']]),
           ylim = c(bounding_atlan$box_out[['ymin']], bounding_atlan$box_out[['ymax']]),
           crs = bounding_atlan$out_crs) 

# add globe# add globevalues()
q_carrier_map_glob <- fishwatchr::add_little_globe(q_carrier_map,
                             main_box = bounding_atlan,
                             globe_rel_size = 0.25,
                             globe_just = 'inside',
                             globe_position = 'upperright')  
  
# save object 
ggsave(q_carrier_map_glob, 
       filename = here::here('outputs','figures','q4_25_proactive',
                             paste('GIN_q4_carrier_lines_highres_v',Sys.Date(),'.png', sep='')), 
       width = 8, 
       height = 10)

```
